### 2020-05-06 presentations/review_response.md
Reorganization (#92)

Reviewer comments:

@helenmiller16's comments

Vignette comments:
* Thank you for pointing out about the special getting started link in pkgdown. I've updated the vignette name and it now appears on the front page of the pkgdown website.
* I've also included a bit more information in the nycflights13 data, a link to the package, as well as references to the functions to set the data up in a database (or with SQLite)

Documentation and examples comments:
* I've added some more documentation as well as a few more exported functions (with documentation). I also added a bit more detail as well.

* I've also added to the examples and made sure that they are runable. One thing I have kept is many of the `\dontrun{}` wrapping around the examples. The reason for keeping that is that many of the tests will interact with either the filesystem (for recording fixtures) or change some aspects of options (for setting mock paths). Neither of which I wanted to do automatically. I did, however, add to the examples so that they can be copied and pasted and run without anything else.

* As for links to httptest, Linking directly in the Rd causes a CMD check error (below) when httptest isn't available, and I didn't think that adding it as a suggest was worth it, I have made sure there are a few links to the CRAN page for httptest, however.

```
N  checking Rd cross-references (3.6s)
   Package unavailable to check Rd xrefs: ‘httptest’
```

Community guidelines comments:
* I've add a contributing guide.

Other comments:
* Starting and stopping mocks. Both reviewers mentioned wanting an additional way to start and stop mocking besides `with_mock_db()`. I've added `start_mock_db()` and `stop_mock_db()` to turn mocking on and off. This way people can step through their tests if they want (and this addresses some of the other comments as well).

* Organization *TODO*

* Debugging: thank you for the suggestion, I've added `set_dittodb_debug_level()` and included some documentation about how to use it and what is printed with debugging turned on.

* I've removed `start_capturing()` entirely, but am using `.Deprecated()` for the deprecation of `.db_mock_paths()`

* Thank you for catching the bug in `redact_columns()`. I intended for `grep` to work there and possibly even match multiple columns, but it would not have done that without a fix. I've not fixed that and added to the documentation how to use regex to specify more than one column at a time.

* Developer setup, I've added a whole vignette devoted to how to develop `dittodb` and to set up testing databases. I've also reorganized some of the setup scripts to make it easier to see which ones to use, how to turn on the tests for those when you're ready. Finally, I've added a method for changing the ports that are used by the test databases.

### 2020-05-06 R/connection.R

@@ -78,72 +78,3 @@ dbMockConnect <- function(drv, ...) {
 
   return(new(mock_class, path = path, original_class = original_class))
 }
-
-
-#' Get the `dbname` from a connection call
-#'
-#' @param dots from the argument being passed to the connection
-#'
-#' @return the name, sanitized if needed
-#'
-#' @keywords internal
-#'
-#' @export
-get_dbname <- function(dots) {
-  # look through dots to grab either dbname or the first unnammed argument
-  named_dbname <- !is.null(dots$dbname) && dots$dbname != ""
-  named_database <- !is.null(dots$Database) && dots$Database != ""
-  unnamed_dbname <- length(dots) > 0 &&
-    (is.null(names(dots[1])) || names(dots[1]) == "")
-  # if there is no name, or it's empty
-  if (named_dbname) {
-    path <- dots$dbname
-  } else if (named_database) {
-    path <- dots$Database
-  } else if (unnamed_dbname) {
-    path <- dots[[1]]
-  } else {
-    stop("There was no dbname, so I don't know where to look for mocks.")
-  }
-  return(db_path_sanitize(path))
-}
-
-
-# DBI methods from the respective DBI DB implementations
-# TODO: make a list of these so that it's not just copy/paste?
-
-#' @rdname mock-db-methods
-#'
-#' @importFrom methods getMethod
-#'
-#' @export
-setMethod(
-  "dbListTables", signature("DBIMockConnection"),
-  function(conn, ...) {
-    getMethod("dbListTables", signature = conn@original_class)(conn, ...)
-  }
-)
-
-#' @rdname mock-db-methods
-#'
-#' @export
-setMethod("dbGetInfo", signature("DBIMockConnection"), function(dbObj, ...) {
-  path <- make_path(dbObj@path, "conInfo", "")
-  return(read_file(find_file(path)))
-})
-
-# TODO: should we also implement signature("DBIMockConnection", "character",
-# "character") most backends warn that it isn't well supported.
-#' @rdname mock-db-methods
-#' @export
-setMethod(
-  "dbWriteTable", signature("DBIMockConnection", "character", "data.frame"),
-  function(conn, name, value, ...) return(TRUE)
-)
-
-#' @rdname mock-db-methods
-#' @export
-setMethod(
-  "dbRemoveTable", signature("DBIMockConnection", "character"),
-  function(conn, name, ...) return(TRUE)
-)

### 2020-05-06 R/dbQueries-Results.R

@@ -73,7 +73,8 @@ setMethod("fetch", signature("DBIMockResult", "missing"), mock_fetch)
 #' @rdname mock-db-methods
 #' @export
 setMethod(
-  "dbClearResult", signature("DBIMockResult"),
+  "dbClearResult",
+  signature("DBIMockResult"),
   function(res, n, ...) return(invisible(TRUE))
 )
 
@@ -81,16 +82,17 @@ setMethod(
 #' @rdname mock-db-methods
 #' @export
 setMethod(
-  "dbHasCompleted", signature("DBIMockResult"),
+  "dbHasCompleted",
+  signature("DBIMockResult"),
   function(res, ...) return(invisible(TRUE))
 )
 
-
 #' @rdname mock-db-methods
 #' @importFrom methods setMethod new
 #' @export
 setMethod(
-  "dbGetQuery", signature("DBIMockRPostgreSQLConnection", "character"),
+  "dbGetQuery",
+  signature("DBIMockRPostgreSQLConnection", "character"),
   function(conn, statement, ...) {
     # TODO: this is really only needed for RPostgreSQL, and even for that, we
     # likely could instead just mock `isPostgresqlIdCurrent` to return a valid
@@ -101,12 +103,12 @@ setMethod(
   }
 )
 
-
 #' @rdname mock-db-methods
 #' @importFrom methods setMethod new
 #' @export
 setMethod(
-  "dbGetQuery", signature("DBIMockRPostgreSQLConnection", "character"),
+  "dbGetQuery",
+  signature("DBIMockRPostgreSQLConnection", "character"),
   function(conn, statement, ...) {
     # TODO: this is really only needed for RPostgreSQL, and even for that, we
     # likely could instead just mock `isPostgresqlIdCurrent` to return a valid
@@ -116,25 +118,3 @@ setMethod(
     return(mock_fetch(res, -1))
   }
 )
-
-# This is only strictly necesary for odbc, RPostgres, RPostgreSQL, and RMariaDB
-# use standard queries to list tables.
-# TODO: investigate if it is better to have a special case for ODBC and use
-# the standard sql for the others or use this code for all.
-#' @rdname mock-db-methods
-#'
-#' @importFrom glue glue
-#'
-#' @export
-setMethod("dbColumnInfo", signature("DBIMockResult"), function(res, ...) {
-  path <- make_path(res@path, "columnInfo", res@hash)
[…]

### 2020-05-06 R/redact.R

@@ -1,31 +1,3 @@
-redact <- function(data, redactors) {
-  columns <- names(redactors)
-  data[, columns] <- lapply(columns, function(x) redactors[[x]](data[, x]))
-  return(data)
-}
-
-standard_redactors <- function(data, columns) {
-  out <- lapply(columns, function(x) {
-    col <- data[[x]]
-
-    if (inherits(col, "integer")) {
-      return(function(data) return(rep(9L, length(data))))
-    } else if (inherits(col, "numeric")) {
-      return(function(data) return(rep(9, length(data))))
-    } else if (inherits(col, "character")) {
-      return(function(data) return(rep("[redacted]", length(data))))
-    } else if (inherits(col, "POSIXct")) {
-      # should this actually be POSIXt? or have a separate POSIXlt?
-      return(function(data) {
-        tzone <- attributes(data)$tzone %||% "EST"
-        return(rep(as.POSIXct("1988-10-11T17:00:00", tz = tzone), length(data)))
-      })
-    }
-  })
-  names(out) <- columns
-  return(out)
-}
-
 #' Redact columns from a dataframe with the default redactors
 #'
 #' This function redacts the columns specified in `columns` in the data given in
@@ -86,4 +58,32 @@ redact_columns <- function(data, columns, ignore.case = TRUE, ...) { # nolint
   columns <- columns[lapply(columns, length) > 0]
 
   return(redact(data, standard_redactors(data, columns)))
+}
+
+redact <- function(data, redactors) {
+  columns <- names(redactors)
+  data[, columns] <- lapply(columns, function(x) redactors[[x]](data[, x]))
+  return(data)
+}
+
+standard_redactors <- function(data, columns) {
+  out <- lapply(columns, function(x) {
+    col <- data[[x]]
+
+    if (inherits(col, "integer")) {
+      return(function(data) return(rep(9L, length(data))))
+    } else if (inherits(col, "numeric")) {
+      return(function(data) return(rep(9, length(data))))
+    } else if (inherits(col, "character")) {
+      return(function(data) return(rep("[redacted]", length(data))))
+    } else if (inherits(col, "POSIXct")) {
+      # should this actually be POSIXt? or have a separate POSIXlt?
+      return(function(data) {
+        tzone <- attributes(data)$tzone %||% "EST"
+        return(rep(as.POSIXct("1988-10-11T17:00:00", tz = tzone), length(data)))
+      })
+    }
+  })
+  names(out) <- columns
+  return(out)
 }

### 2020-05-06 presentations/review_response.md
capture_db_requests

@@
 
-* Organization *TODO*
+* Organization I've reorganized some of the methods to be more thematic and all of the methods that work with the various `DBI` methods (e.g.
+`DBI::dbQueries-Results.R` for query and result focused methods).
 
@@
 Finally, I've added a method for changing the ports that are used by the test databases.
+
+@etiennebr's comments
+
+Installation instructions:
+* I've added a new givnette that describes the process to set up development databases, various configuration options (when, why, and how to turn on or off tests locally).
+I've also clarified and described more about what the databse setup scripts are for (and warned against running ones that are intended for / needed for CI compared to ones that are intended for running locally)
+
+Improved vignettes
+*TODO*
+>  I would suggest that a vignette walking the user through the
+full process of testing during package development would make adoption much
+easier. I'll comment further on this later, but I could not figure a smooth
+workflow, which I'm sure the authors have figured out.
+> 
+> I find the diversity of examples in the vignettes and the README very
+relevant, but as I mentionned above, database setup could be improved to
+accelerate the users. I would suggest to:
+> 
+> Provide a simple example using maybe a simple sqlite file in the readme;
+Provide instructions to run a docker container in the vignettes.
+
+Community Guidlines:
+* I've added a contributing guidlines document, thanks for noticing this oversight.
+
+Automated Tests:
+* I've added more description of what tests are not run by defualt locally (which makes coverage lower like you noted).
+To get full coverage one has to run all of the database backends during tests and turn on those tests with environment variables (both to make local development easier when one is not messing with some backends as well as to make sure these tests are not run on CRAN).
+The CI setup turns these on (and sets up the databses) and the coverage figure comes from there.
+
+* Thanks for noticing I wasn't recommending the correct `.sh` scripts in my very brief discussion in the readme.
+I've expanded that discussion in the new development vignette and I renamed some of those scripts to hopefully be more user-friendly and obvious.
+
+Workflow:
+*TODO* 
+> As I mentioned earlier, I could understand the vignettes and the examples, but
+> I'm not sure I understand dittodb intented package development workflow. By
+> looking at the package's own tests, I think I could grapple some ideas, but I
+> still find the ergonomic of the package could be better (or explained). Maybe I
+> should just get more familiar with it, but I feel like I spent a larger amount
+> of time playing with it than most potential users would --out of pure
+> motivation, mind you.
+> 
+> Here's how I used dittodb:
+> 
+> add a start and stop line at the beginning and the end of the database tests
+> run the tests manually
+> remove the start and stop line
+> wrap all the code in a with_mock_db({})
+> repeat every time you add a test (and make sure contributors know the gymnastic)
+> Here are my pain points:
+> 
+> Debugging is harder, because I can't step through the tests
+> We need to change many lines of code in different places every time a test
+> changes, which makes it error prone
+> The commit that adds dittodb change all the lines in a test file
+> (re-indent), which burries the changes in another layer (maybe that's just me)
+> What I would like is to:
+> 
+> Make it possible to run tests line-by-line
+> Set it up once and not think about it (especially other contributors)
+> Have minimal changes in the code
+> 
+> I came up with a suggestion, but I have no idea of the feasability (although I
+> think it could be possible). Maybe dittodb could strictly modify the database
+> connection with a custom e.g. dittodb_con class and use normal dispatch to
+> catch results. So if the connection is possible, it connects to the database. If
+> the connection is not possible, it will use fixtures. That way if the dev has a
+> working database connection, it will run the tests against the database and
+> write fixtures, but if the connection is impossible, it will run against the
+> fixture. That way we can track the response by committing fixtures (which is
+> cool) and see if a change requires a change in fixtures (and it's transparent).
+
+Thank you for this suggestion.
+I thought about this a lot and one of the things I did try out implementing was this kind of dual-use class/connector that would use mocks if available and then use the database if not.
+It turned out that it actually ended up getting pretty confusing when it was using which connector under the hood, especially when there were different failures on CI compared to locally.
+I also wanted to avoid needing to make any operational code changes to start using `dittodb` (with the current architecture, the only time the `dittodb` classes are used or needed is when tests are run).
+
+I did make a number of changes that I think address the main struggles here: there is now a `start_mock_db()` and `stop_mock_db()` that make it easier to step through tests line-by-line without needing to use `browser()` or breakpoints.
+I've added a bit more to the getting started vignette to show an iterative process of the record - test process I use with dittodb
+
+* wrapper for capturing requests 
+Thank you for this suggestion, I've implemented this with `capture_db_requests({})` which can be wrapped around any code that you want to record interactions for.
+
+Data format:
+> I find that using an R structure to store the connection info and the responses,
+> although natural to the R environment, makes it slightly harder to see changes
+> in the data when tracking it with git. I wonder if responses shouldn't be yaml
+> or csv files, just to make them easier to track with git (to explicitly see a
+> line change).
+
+Yes, I've actually thought about this a little bit already and you note the pretty clear tension involved in this.
+Ideally, the fixtures would be plain text and easy to see if things are changing in gitdiffs.
+Ideally something like a CSV would be great, and I tried that initially, but there's some type-loss in CSVs that require some kind of sidecar metadata file.
+I've also looked in to using something like [csvy](https://cran.r-project.org/web/packages/csvy/index.html) which has a metadata header that would work well, but if that is a dependency it also means adding `data.table` (and it's dependencies) as a dependency to `dittodb`.
+
+I think a better approach might be to replicate some of what csvy is doing inside of `dittodb` so we don't take on another dependency and we get the nice result of having CSV (like) fixture files.
+Collaborators have also wanted to include the ability to use other kinds of serializers for cases when they want to save a lot of data.
+This is something I don't necesarily want to fully support out of the box / make super easy because I think like you mention having small, digestable, readable fixtures is important to making good tests, it would be nice of us to provide a hook that someone could use if they wanted to to make their own serializing and deserializing functions as well.
+
+I have been tracking thoughts and ideas here: https://github.com/jonkeane/dittodb/issues/61 I agree that this is something that would be really good to resolve, but since it's not a blocker to functionality right now, think it would be good to add this in as a feature in a later release.
+
+> Also, since the fixtures are .R files, they go through the linter, which
+> raises errors. It is probably possible to configure, though.
+
+Yeah, that's an issue. I've added an issue to investigate the ways to address this.
+https://github.com/jonkeane/dittodb/issues/94 Since it's not a blocker, I'm going to save this enhancement for a future release, but thank you for pointing it out and the suggestion!
+
+* I wondered why is `.db_mock_path()` prefixed with a `.`?
+I've changed this. It was originally based off of httptest's `.mockPaths()` which
+took inspiration (and interface) from `.libPaths()`.
+At this point I think the lineage is too tenuous to make it useful to have the name the way it is, so I've removed the dot entirely.
+Thanks for commenting on this, a great example of something only making sense through the developer/creator's eyes that would be mindboggling for most people using it.
+
+* `start_capturing()` and `stop_capturing()`
+Thank you for the suggestion to use `.Deprecated()` or remove them.
+Like you mentioned, this is still in development and they have been soft-deprecated for a while so I just removed them.
+Though I did use `.Deprecated()` when deprecating `.db_mock_paths()` above.
+
+* What's the relation between rstudio/dbtest and jonkeane/dittodb? Maybe it
+doesn't even have to be mentionned?
+There isn't any relation, I had originally called `dittodb` `dbtest` (after `httptest`) but @maelle pointed out that `rstudio/dbtest` already existed (though was not on CRAN)
+
+* Fixtures vs. snapshots
+I had origionally conceived of this as making it easier to understand (I know that beginners to testing can find the multiplicity of terms fixture, mock, stud, harness, etc.
+confusing).
+I thought using snapshot in the getting started would be helpful, but I agree with you that it wasn't used particularly well.
+What I've done is used `snapshot` in the very beginning to describe it abstractly and then specifically name it fixture and use fixture throughout elsewhere.

### 2020-05-06 R/capture-requests.R

@@ -4,14 +4,19 @@
 #' the responses from the database for use in crafting tests.
 #'
 #' You can start capturing with `start_db_capturing()` and end it with
-#' `stop_db_capturing`. All queries run against a database will be executed like
+#' `stop_db_capturing()`. All queries run against a database will be executed like
 #' normal, but their responses will be saved to the mock path given, so that if
 #' you use the same queries later inside of a [`with_mock_db`] block, the
 #' database functions will return as if they had been run against the database.
 #'
+#' Alternatively, you can wrap the code that you are trying to capture in the
+#' function `capture_db_requests({...})` this does the same thing as
+#' `start_db_capturing()` and `stop_db_capturing()` but without needing to
+#' remember to stop the recording.
+#'
 #' You can redact certain columns using the `redact_columns` argument. This will
 #' replace the values in the column with a generic redacted version. This works
-#' by always passing the data being saved through [`redact_columns()`].
+#' by always passing the data being saved through [`redact_columns`].
 #'
 #' _note_ You should always call [`DBI::dbConnect`] inside of the capturing
 #' block. When you connect to the database, dittodb sets up the mocks for the
@@ -261,6 +266,19 @@ stop_db_capturing <- function() {
   }
 
   remove_redactor()
+}
+
+#' @rdname capture_requests
+#' @export
+capture_db_requests <- function(expr, path, redact_columns = NULL) {
+  start_db_capturing(redact_columns = redact_columns)
+  on.exit(stop_db_capturing())
+  where <- parent.frame()
+  if (!missing(path)) {
+    with_mock_path(path, eval(expr, where))
+  } else {
+    eval(expr, where)
+  }
 }
 
 # for detecting if a particular method has been loaded

### 2020-05-06 R/dbMisc.R

@@ -1,3 +1,6 @@
+#' @include dbQueries-Results.R
+NULL
+
 # Miscellaneous DBI methods from the respective DBI DB implementations
 # TODO: make a list of these so that it's not just copy/paste?
 

### 2020-05-07 R/dbQueries-Results.R
Capture db requests (#95)

@@ -1,3 +1,6 @@
+#' @include driver-specific-connections.R
+NULL
+
 #' @rdname mock-db-methods
 #' @import DBI
 #' @export

### 2020-05-07 inst/nycflight_mocks/nycflights/SELECT-ef6317.R

@@ -1,2 +1,2 @@
-structure(list(carrier = "9E", name = "Endeavor Air Inc."), class = "data.frame", row.names = c(NA, 
+structure(list(carrier = "9E", name = "Endeavor Air Inc."), class = "data.frame", row.names = c(NA,
 -1L))

### 2020-05-07 tests/testthat/test-capture-requests.R

@@ -42,6 +42,35 @@ with_mock_path(path = file.path(temp_dir, "recording_tracing"), {
   )
 
   stop_db_capturing()
+
+  capture_db_requests({
+    test_that("DBI and the top-most dbSenQuery has been traced", {
+      # the first instance of dbSendQuery is mocked:
+      expect_s4_class(getAnywhere("dbSendQuery")[1], "standardGenericWithTrace")
+
+      # the DBI namespace instance of dbQuery is also mocked:
+      dbi_ind <- which(getAnywhere("dbSendQuery")$where == "namespace:DBI")
+      expect_s4_class(
+        getAnywhere("dbSendQuery")[dbi_ind],
+        "standardGenericWithTrace"
+      )
+    })
+  })
+
+  # while setting a path
+  capture_db_requests(path = tempdir(), {
+    test_that("DBI and the top-most dbSenQuery has been traced", {
+      # the first instance of dbSendQuery is mocked:
+      expect_s4_class(getAnywhere("dbSendQuery")[1], "standardGenericWithTrace")
+
+      # the DBI namespace instance of dbQuery is also mocked:
+      dbi_ind <- which(getAnywhere("dbSendQuery")$where == "namespace:DBI")
+      expect_s4_class(
+        getAnywhere("dbSendQuery")[dbi_ind],
+        "standardGenericWithTrace"
+      )
+    })
+  })
 })
 
 test_that("set_redactor sets and unsets", {

### 2020-05-07 presentations/review_response.md
Capture db requests (#95)
formatting

--- 2020-05-06 presentations/review_response.md
@@
 
-@helenmiller16's comments
+# @helenmiller16's comments
 
-Vignette comments:
-* Thank you for pointing out about the special getting started link in pkgdown. I've updated the vignette name and it now appears on the front page of the pkgdown website.
-* I've also included a bit more information in the nycflights13 data, a link to the package, as well as references to the functions to set the data up in a database (or with SQLite)
+## Vignette comments
+Thank you for pointing out about the special getting started link in pkgdown. I've updated the vignette name and it now appears on the front page of the pkgdown website.
 
-Documentation and examples comments:
-* I've added some more documentation as well as a few more exported functions (with documentation). I also added a bit more detail as well.
+I've also included a bit more information in the nycflights13 data, a link to the package, as well as references to the functions to set the data up in a database (or with SQLite)
 
-* I've also added to the examples and made sure that they are runable.
+## Documentation and examples comments
+I've added some more documentation as well as a few more exported functions (with documentation). I also added a bit more detail as well.
+
+I've also added to the examples and made sure that they are runable.
 One thing I have kept is many of the `\dontrun{}` wrapping around the examples.
@@
 
-* As for links to httptest, Linking directly in the Rd causes a CMD check error (below) when httptest isn't available, and I didn't think that adding it as a suggest was worth it, I have made sure there are a few links to the CRAN page for httptest, however.
+As for links to httptest, Linking directly in the Rd causes a CMD check error (below) when httptest isn't available, and I didn't think that adding it as a suggest was worth it, I have made sure there are a few links to the CRAN page for httptest, however.
 
@@
 
-Community guidelines comments:
-* I've add a contributing guide.
+## Community guidelines comments
+I've add a contributing guide.
 
-Other comments:
-* Starting and stopping mocks.
+## Other comments
+Starting and stopping mocks.
 Both reviewers mentioned wanting an additional way to start and stop mocking besides `with_mock_db()`.
@@
 
-* Organization *TODO*
+## Organization 
+I've reorganized some of the methods to be more thematic and all of the methods that work with the various `DBI` methods (e.g. `DBI::dbQueries-Results.R` for query and result focused methods).
 
-* Debugging: thank you for the suggestion, I've added `set_dittodb_debug_level()` and included some documentation about how to use it and what is printed with debugging turned on.
+## Debugging
+Thank you for the suggestion, I've added `set_dittodb_debug_level()` and included some documentation about how to use it and what is printed with debugging turned on.
 
-* I've removed `start_capturing()` entirely, but am using `.Deprecated()` for the deprecation of `.db_mock_paths()`
+## Use of `.Deprecated()`
+I've removed `start_capturing()` entirely, but am using `.Deprecated()` for the deprecation of `.db_mock_paths()`
 
-* Thank you for catching the bug in `redact_columns()`.
+## `redact_columns()` bug
+Thank you for catching the bug in `redact_columns()`.
 I intended for `grep` to work there and possibly even match multiple columns, but it would not have done that without a fix.
@@
 
-* Developer setup, I've added a whole vignette devoted to how to develop `dittodb` and to set up testing databases.
+## Developer setup
+Developer setup, I've added a whole vignette devoted to how to develop `dittodb` and to set up testing databases.
 I've also reorganized some of the setup scripts to make it easier to see which ones to use, how to turn on the tests for those when you're ready.
 Finally, I've added a method for changing the ports that are used by the test databases.
+
+# @etiennebr's comments
+
+## Installation instructions
+I've added a new vignette that describes the process to set up development databases, various configuration options (when, why, and how to turn on or off tests locally).
+I've also clarified and described more about what the database setup scripts are for (and warned against running ones that are intended for / needed for CI compared to ones that are intended for running locally)
+
+## Improved vignettes
+I've added a bit more to the getting started vignette to show an iterative process of the record - test process I use with dittodb.
+I've also added a developer vignette to help getting started with development.
+
+## Community Guidelines
+I've added a contributing guidelines document, thanks for noticing this oversight.
+
+## Automated Tests
+I've added more description of what tests are not run by default locally (which makes coverage lower like you noted).
+To get full coverage one has to run all of the database backends during tests and turn on those tests with environment variables (both to make local development easier when one is not messing with some backends as well as to make sure these tests are not run on CRAN).
+The CI setup turns these on (and sets up the databases) and the coverage figure comes from there.
+
+Thanks for noticing I wasn't recommending the correct `.sh` scripts in my very brief discussion in the readme.
+I've expanded that discussion in the new development vignette and I renamed some of those scripts to hopefully be more user-friendly and obvious.
+
+## Workflow
+Thank you for this suggestion.
+I thought about this a lot and one of the things I did try out implementing was this kind of dual-use class/connector that would use mocks if available and then use the database if not.
+It turned out that it actually ended up getting pretty confusing when it was using which connector under the hood, especially when there were different failures on CI compared to locally.
+I also wanted to avoid needing to make any operational code changes to start using `dittodb` (with the current architecture, the only time the `dittodb` classes are used or needed is when tests are run).
+
+I did make a number of changes that I think address the main struggles here: there is now a `start_mock_db()` and `stop_mock_db()` that make it easier to step through tests line-by-line without needing to use `browser()` or breakpoints.
+I've added a bit more to the getting started vignette to show an iterative process of the record - test process I use with dittodb
+
+## wrapper for capturing requests 
+Thank you for this suggestion, I've implemented this with `capture_db_requests({})` which can be wrapped around any code that you want to record interactions for.
+
+## Data format
+Yes, I've actually thought about this a little bit already and you note the pretty clear tension involved in this.
+Ideally, the fixtures would be plain text and easy to see if things are changing in gitdiffs.
+Ideally something like a CSV would be great, and I tried that initially, but there's some type-loss in CSVs that require some kind of sidecar metadata file.
+I've also looked in to using something like [csvy](https://cran.r-project.org/web/packages/csvy/index.html) which has a metadata header that would work well, but if that is a dependency it also means adding `data.table` (and it's dependencies) as a dependency to `dittodb`.
+
+I think a better approach might be to replicate some of what csvy is doing inside of `dittodb` so we don't take on another dependency and we get the nice result of having CSV (like) fixture files.
+Collaborators have also wanted to include the ability to use other kinds of serializers for cases when they want to save a lot of data.
+This is something I don't necessarily want to fully support out of the box / make super easy because I think like you mention having small, digestable, readable fixtures is important to making good tests, it would be nice of us to provide a hook that someone could use if they wanted to to make their own serializing and deserializing functions as well.
+
+I have been tracking thoughts and ideas here: https://github.com/jonkeane/dittodb/issues/61 I agree that this is something that would be really good to resolve, but since it's not a blocker to functionality right now, think it would be good to add this in as a feature in a later release.
+
+### About lintr complaining about some of the fixtures
+Yeah, that's an issue. I've added an issue to investigate the ways to address this.
+https://github.com/jonkeane/dittodb/issues/94 Since it's not a blocker, I'm going to save this enhancement for a future release, but thank you for pointing it out and the suggestion!
+
+## I wondered why is `.db_mock_path()` prefixed with a `.`?
+I've changed this. It was originally based off of httptest's `.mockPaths()` which
+took inspiration (and interface) from `.libPaths()`.
+At this point I think the lineage is too tenuous to make it useful to have the name the way it is, so I've removed the dot entirely.
+Thanks for commenting on this, a great example of something only making sense through the developer/creator's eyes that would be mind boggling for most people using it.
+
+## `start_capturing()` and `stop_capturing()`
+Thank you for the suggestion to use `.Deprecated()` or remove them.
+Like you mentioned, this is still in development and they have been soft-deprecated for a while so I just removed them.
+Though I did use `.Deprecated()` when deprecating `.db_mock_paths()` above.
+
+## What's the relation between rstudio/dbtest and jonkeane/dittodb? Maybe it
+doesn't even have to be mentioned?
+There isn't any relation, I had originally called `dittodb` `dbtest` (after `httptest`) but @maelle pointed out that `rstudio/dbtest` already existed (though was not on CRAN).
+There isn't really any other connection and they are looking to solve very different problems.
+I can add a section about that if you think it's important.
+
+## Fixtures vs. snapshots
+I had originally conceived of this as making it easier to understand (I know that beginners to testing can find the multiplicity of terms fixture, mock, stud, harness, etc.
+confusing).
+I thought using snapshot in the getting started would be helpful, but I agree with you that it wasn't used particularly well.
+What I've done is used `snapshot` in the very beginning to describe it abstractly and then specifically name it fixture and use fixture throughout elsewhere.

### 2020-05-11 vignettes/travelling/resultInfo-6f7e1a.R
Use a different dbplyr set of verbs to avoid a lifecycle deprecation in progress

@@ -1,0 +1,18 @@
+list(statement = "SELECT * FROM \"flights\" AS \"zzz13\" WHERE 0=1", 
+    isSelect = 1L, rowsAffected = -1L, rowCount = 0L, completed = 0L, 
+    fieldDescription = list(list(name = c("year", "month", "day", 
+    "dep_time", "sched_dep_time", "dep_delay", "arr_time", "sched_arr_time", 
+    "arr_delay", "carrier", "flight", "tailnum", "origin", "dest", 
+    "air_time", "distance", "hour", "minute", "time_hour"), Sclass = c(13L, 
+    13L, 13L, 13L, 13L, 14L, 13L, 13L, 14L, 16L, 13L, 16L, 16L, 
+    16L, 14L, 14L, 14L, 14L, 16L), type = c(23L, 23L, 23L, 23L, 
+    23L, 701L, 23L, 23L, 701L, 25L, 23L, 25L, 25L, 25L, 701L, 
+    701L, 701L, 701L, 1184L), len = c(4L, 4L, 4L, 4L, 4L, 8L, 
+    4L, 4L, 8L, -1L, 4L, -1L, -1L, -1L, 8L, 8L, 8L, 8L, 8L), 
+        precision = c(-1L, -1L, -1L, -1L, -1L, -1L, -1L, -1L, 
+        -1L, -1L, -1L, -1L, -1L, -1L, -1L, -1L, -1L, -1L, -1L
+        ), scale = c(-1L, -1L, -1L, -1L, -1L, -1L, -1L, -1L, 
+        -1L, -1L, -1L, -1L, -1L, -1L, -1L, -1L, -1L, -1L, -1L
+        ), nullOK = c(TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, 
+        TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, 
+        TRUE, TRUE, TRUE))))

### 2020-05-11 tests/testthat/test-dbi-generic-integration.R
A few more updates

@@ -11,7 +11,7 @@ db_pkgs <- list(
     RMariaDB::MariaDB(),
     dbname = "nycflights",
     host = "127.0.0.1",
-    username = "travis",
+    username = db_user,
     password = "",
     port = testing_port("maria")
   )),

### 2020-05-29 presentations/satRday2020/satRday2020.Rmd
satRday presentation

---
title: "dittodb"
subtitle: "making testing databases easy"
author: "Jonathan Keane"
institute: "Socure"
date: "2020-05-30 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["xaringan-themer.css", "Azuro.css"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: ""
---
background-image: url("images/IMG_5793.png")
background-position: 50% 50%
background-size: cover

class: inverse, center, top

# What is testing?

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(emojifont) 
library(xaringanthemer)
style_mono_accent(
  base_color = "#1c5253",
  header_font_family = "Azuro",
  text_font_family = "Azuro",
  code_font_google   = google_font("Fira Mono"),
  text_font_size = "1.25rem",
  colors = c(white = "#FFFFFF", gray = "#898C9C"),
  header_h2_font_size = "1.75rem",
  header_h3_font_size = "1.25rem",
  extra_css = list(
    ".large" = list(
      "font-size" = "2.75rem"
    ),
    ".inverse > h1 > code" = list(
      "color" = "var(--inverse-header-color)"
    ),
    ".colophon" = list(
      "font-size" = "0.9rem",
      "position" = "absolute",
      "bottom" = 0
    ),
    ".flex-box" = list(
    "display" = "flex",
    "flex-direction" = "column",
    "justify-content" = "space-between",
    "height" = "70%"
    ),
    # the first p of .flext-box should have no top-margin
    ".flex-box > p:first-child" = list(
      "margin-top" = 0
    ),
    ".flex-box > p:last-of-type" = list(
      "padding-bottom" = "1em"
    ),
    ".seventyfive" = list(
      "width" = "75%",
      "margin" = "0 auto"
    )
  )
)
```

---
class: inverse, center, middle

## A way to check that the code you wrote is doing what you expect it to.

---
# Easier said than done

<br /><br />
Any test is better than no tests

--
<br /><br />

but a good test is worth its (metaphorical) weight in gold

---
# A good test is ...
* quick to run
* expressive
* doesn't require special set up

--

# But databases are ...
* (relatively) slow
* rely on external state or set up
* requires a connection or custom setup

---
# CI + DBs = ☠️

Continuous integration (like GitHub Actions, Travis, AppVeyor) is wonderful, 
you can run your code on someone else's ☁️ 💻 
<br/> <br/>

--

But then you're running your code in an environment you have to set up.
--
 That you can't interactively iterate on.
<br/> <br/>

--

Even installing R dependencies can be a pain.

---
background-image: url("images/db-test-ci-db-hard-more-again.png")
background-position: 50% 50%
background-size: contain
class: center, bottom

---
background-image: url("images/db-test-ci-db-hard-more.png")
background-position: 0% 20%
background-size: contain
class: center, bottom

--

# I've slogged through this <br/> so you don't have to

---
background-image: url("images/_DSC1176.png")
background-position: 50% 50%
background-size: cover
class: center, top

# How does `dittodb` help?

---
# Imagine we had a function

```r
#' Get random airline(s)
#' ...
get_an_airline <- function(n = 1) {
  con <- DBI::dbConnect(RPostgres::Postgres(), dbname = "nycflights")
  on.exit(DBI::dbDisconnect(con))

  query <- paste0(
    "SELECT carrier, name FROM airlines ",
    "ORDER BY random() LIMIT ", 
    n
  )

  out <- dbGetQuery(con, query)

  if (out$name == "Testy McAirline") {
    stop("This is the test airline 🙃")
  }

  return(out)
}
```
---
# How can we test it?
Locally is “easy” we:
 * setup a local postgres server
 * make sure the correct users exist
 * add the test data
 * profit

--

On CI we “just” do the same:  
 * setup a local postgres server
 * make sure the correct users exist
 * add the test data
--
<br/>
<div class = "large">❌ ❌ ❌ ❌ ☠️ ☠️ ☠️ ❌ ❌ ❌ ❌</div>

---
# `dittodb` lets you ...

Write tests that act like they are connected to a real-live database using `with_mock_db({...})`

```r
with_mock_db({
  test_that("We get one airline", {
    one_airline <- get_an_airline()
    expect_is(one_airline, "data.frame")
    expect_equal(nrow(one_airline), 1)
    expect_equal(one_airline$carrier, "9E")
    expect_equal(one_airline$name, "Endeavor Air Inc.")
  })
})
```

---

# Testing terminology aside

* mocks

* fixtures

* stubs

* spies

* fakes

* `r emoji("scream")`

???

* mocks -- objects pre-programmed with expectations which form a specification 
* fixtures -- data used by mocked objects to configure them or provide info 
* stubs -- provide canned answers to calls made during the test, usually not responding at all to anything outside what's programmed in for the test.
* spies -- stubs, but keep and provide info about how and if they were called
* fakes -- objects actually have working implementations, but usually take some shortcut which makes them not suitable for production (an in memory database is a good example)

Much of the above is from https://www.martinfowler.com/articles/mocksArentStubs.html

---

# Testing terminology aside

* mocks

* fixtures

.gray[
* stubs

* spies

* fakes

* `r emoji("scream")`
]

???

If <5 minutes type 26 to go to the next section

---
background-image: url("images/_DSC1098.png")
background-position: 50% 50%
background-size: cover
class: center, top

# Demo

---
# Mandatory plug
.flex-box[
## Socure is hiring — [socure.com/about/careers](https://www.socure.com/about/careers)

.center.seventyfive[![](https://www.socure.com/hubfs/Assets_2018/SOC-logo-color.svg)]
]

---

# Thanks!
.flex-box[
`dittodb` lives at [_dittodb.jonkeane.com_](https://dittodb.jonkeane.com)

Install `dittodb` with `remotes::install_github("jonkeane/dittodb")`

Extra special thanks to Mauricio Vargas @pachamaltese and thanks to [`httptest`](https://enpiar.com/r/httptest) for inspiration.

@jonkeane 
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;
[_jonkeane.com_](https://jonkeane.com) 
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;
[github.com/jonkeane](https://github.com/jonkeane)

.colophon[
created with the R package [**xaringan**](https://github.com/yihui/xaringan) · all photos taken by Jonathan Keane, all rights reserved <br />
presentation slides + content (except for photos) are licensed under [CC BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/) <br />
]
]

---
# `dittodb` lets you ...

Write tests that include edge cases that “shouldn't” “happen” in your databse.

```r
with_mock_path(path = "error_db_fixt/", {
  with_mock_db({
    test_that("We get one airline", {
      expect_error(
        get_an_airline(),
        "This is the test airline \U1F643
      )
    })
  })
})
```

---
# Capturing DB interactions

Capture database interactions so that writing and editing the above is easier.

```r
capture_db_requests({
  one_airline <- get_an_airline()
})
```

Where `one_airline` is

```r
  carrier                 name
1      AS Alaska Airlines Inc.
```

---
# Capturing DB interactions

This response is saved to `testthat/tests/nycflights` in a file called `SELECT-c3427d.R`:

```r
structure(
  list(carrier = "AS", name = "Alaska Airlines Inc."), 
  class = "data.frame", 
  row.names = c(NA, -1L)
)
```

--

The path is `testthat/tests` and then the db name `nycflights` being connected to.

--

The filename starts with the SQL verb `SELECT`, followed by a hash that is unique to the query.

???

Because the hash is unique per-query that means this particular query will always return the same thing each time. But there are ways around this, for example by using a different mock paths.

---
# Mandatory plug
.flex-box[
## Socure is hiring — [socure.com/about/careers](https://www.socure.com/about/careers)

.center.seventyfive[![](https://www.socure.com/hubfs/Assets_2018/SOC-logo-color.svg)]
]

---

# Thanks!
.flex-box[
`dittodb` lives at [_dittodb.jonkeane.com_](https://dittodb.jonkeane.com)

Install `dittodb` with `remotes::install_github("jonkeane/dittodb")`

Extra special thanks to Mauricio Vargas @pachamaltese and thanks to [`httptest`](https://enpiar.com/r/httptest) for inspiration.

@jonkeane 
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;
[_jonkeane.com_](https://jonkeane.com) 
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;
[github.com/jonkeane](https://github.com/jonkeane)

.colophon[
slides created via the R package [**xaringan**](https://github.com/yihui/xaringan) · photos taken by Jonathan Keane, all rights reserved <br />
presentation slides + content (except for photos) are licensed under [CC BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/) <br />
]
]

### 2020-05-29 presentations/satRday2020/satRday2020.Rmd
some more changes

@@
 subtitle: "making testing databases easy"
-author: "Jonathan Keane"
-institute: "Socure"
+author: "Jonathan Keane · Socure"
+institute: "Chicago satRdays 2020"
 date: "2020-05-30 (updated: `r Sys.Date()`)"
@@
   colors = c(white = "#FFFFFF", gray = "#898C9C"),
-  header_h2_font_size = "1.75rem",
-  header_h3_font_size = "1.25rem",
   extra_css = list(
@@
       "margin" = "0 auto"
+    ),
+    ".title-slide h1" = list(
+      "font-size" = "4rem",
+      "margin-bottom" = "0rem"
+      ),
+    ".title-slide h2" = list(
+      "font-size" = "1.75rem",
+      "margin-top" = "0rem",
+      "margin-bottom" = "4rem"
+      ),
+    ".title-slide h3" = list(
+      "font-size" = "1.75rem",
+      "margin-block-start" = "0rem",
+      "margin-block-end" = "0rem"
+      ),
+    ".title-slide > h3:last-of-type" = list(
+      "font-size" = "1rem",
+      "margin-block-start" = "4rem",
+      "margin-block-end" = "2rem"
     )
@@
 
-Write tests that act like they are connected to a real-live database using `with_mock_db({...})`
+Write tests that act like they are connected to a real-live database using 
+`with_mock_db({...})` without ever having to set one up.
+
+<br/ >
 
@@
 
-???
-
-If <5 minutes type 26 to go to the next section
-
 ---
@@
 
----
-# Mandatory plug
-.flex-box[
-## Socure is hiring — [socure.com/about/careers](https://www.socure.com/about/careers)
+???
 
-.center.seventyfive[![](https://www.socure.com/hubfs/Assets_2018/SOC-logo-color.svg)]
-]
-
----
-
-# Thanks!
-.flex-box[
-`dittodb` lives at [_dittodb.jonkeane.com_](https://dittodb.jonkeane.com)
-
-Install `dittodb` with `remotes::install_github("jonkeane/dittodb")`
-
-Extra special thanks to Mauricio Vargas @pachamaltese and thanks to [`httptest`](https://enpiar.com/r/httptest) for inspiration.
-
-@jonkeane 
-&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;
-[_jonkeane.com_](https://jonkeane.com) 
-&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;
-[github.com/jonkeane](https://github.com/jonkeane)
-
-.colophon[
-created with the R package [**xaringan**](https://github.com/yihui/xaringan) · all photos taken by Jonathan Keane, all rights reserved <br />
-presentation slides + content (except for photos) are licensed under [CC BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/) <br />
-]
-]
-
----
-# `dittodb` lets you ...
-
-Write tests that include edge cases that “shouldn't” “happen” in your databse.
-
-```r
-with_mock_path(path = "error_db_fixt/", {
-  with_mock_db({
-    test_that("We get one airline", {
-      expect_error(
-        get_an_airline(),
-        "This is the test airline \U1F643
-      )
-    })
-  })
-})
-```
+If doing the demo, jump to slide 30
 
@@
 ```
+
+<br />
 
@@
 ---
+# `dittodb` lets you ...
+.flex-box[
+So you can write your test like this
+
+```r
+with_mock_db({
+  test_that("We get one airline", {
+    one_airline <- get_an_airline()
+    expect_is(one_airline, "data.frame")
+    expect_equal(nrow(one_airline), 1)
+    expect_equal(one_airline$carrier, "9E")
+    expect_equal(one_airline$name, "Endeavor Air Inc.")
+  })
+})
+```
+
+.pull-right[... and it will run anywhere!]
+]
+
+---
+# `dittodb` lets you ...
+
+Write tests that include edge cases that “shouldn't” “happen” in your databse.
+
+```r
+with_mock_path(path = "error_db_fixt/", {
+  with_mock_db({
+    test_that("We get one airline", {
+      expect_error(
+        get_an_airline(),
+        "This is the test airline \U1F643
+      )
+    })
+  })
+})
+```
+---
+background-image: url("images/_DSC1098.png")
+background-position: 50% 50%
+background-size: cover
+class: center, top
+
+# It really is as easy as that!
+
+---
 # Mandatory plug
@@
 .colophon[
-slides created via the R package [**xaringan**](https://github.com/yihui/xaringan) · photos taken by Jonathan Keane, all rights reserved <br />
+created with the R package [**xaringan**](https://github.com/yihui/xaringan) · all photos taken by Jonathan Keane, all rights reserved <br />
 presentation slides + content (except for photos) are licensed under [CC BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/) <br />

### 2020-06-06 pkgdown/extra.js
Tabbing in pkgdown!

@@ -1,0 +1,151 @@
+/**
+ * adapted from rmarkdown/inst/rmd/h/navigation-1.1/tabsets.js
+ *
+ * jQuery Plugin: Sticky Tabs
+ *
+ * @author Aidan Lister <aidan@php.net>
+ * adapted by Ruben Arslan to activate parent tabs too
+ * http://www.aidanlister.com/2014/03/persisting-the-tab-state-in-bootstrap/
+ */
+(function($) {
+  "use strict";
+  $.fn.rmarkdownStickyTabs = function() {
+    var context = this;
+    // Show the tab corresponding with the hash in the URL, or the first tab
+    var showStuffFromHash = function() {
+      var hash = window.location.hash;
+      var selector = hash ? 'a[href="' + hash + '"]' : 'li.active > a';
+      var $selector = $(selector, context);
+      if($selector.data('toggle') === "tab") {
+        $selector.tab('show');
+        // walk up the ancestors of this element, show any hidden tabs
+        $selector.parents('.section.tabset').each(function(i, elm) {
+          var link = $('a[href="#' + $(elm).attr('id') + '"]');
+          if(link.data('toggle') === "tab") {
+            link.tab("show");
+          }
+        });
+      }
+    };
+
+
+    // Set the correct tab when the page loads
+    showStuffFromHash(context);
+
+    // Set the correct tab when a user uses their back/forward button
+    $(window).on('hashchange', function() {
+      showStuffFromHash(context);
+    });
+
+    // Change the URL when tabs are clicked
+    $('a', context).on('click', function(e) {
+      history.pushState(null, null, this.href);
+      showStuffFromHash(context);
+    });
+
+    return this;
+  };
+}(jQuery));
+
+window.buildTabsets = function(tocID) {
+
+  // build a tabset from a section div with the .tabset class
+  function buildTabset(tabset) {
+
+    // check for fade and pills options
+    var fade = tabset.hasClass("tabset-fade");
+    var pills = tabset.hasClass("tabset-pills");
+    var navClass = pills ? "nav-pills" : "nav-tabs";
+
+    // determine the heading level of the tabset and tabs
+    var match = tabset.attr('class').match(/level(\d) /);
+    if (match === null)
+      return;
+    var tabsetLevel = Number(match[1]);
+    var tabLevel = tabsetLevel + 1;
+
+    // find all subheadings immediately below
+    var tabs = tabset.find("div.section.level" + tabLevel);
[…]

### 2020-06-06 R/capture-requests.R
Add multiple db backends to readme/vignettes

@@ -37,7 +37,7 @@
 #' # Temporary files for examples
 #' nycflights_path <- tempfile()
 #'
-#' con <- nycflights13_sqlite(location = nycflights_path)
+#' con <- nycflights13_create_sqlite(location = nycflights_path)
 #' dbDisconnect(con)
 #'
 #' start_db_capturing()

### 2020-06-06 R/nycflights13-sql.R

@@ -45,13 +45,13 @@
 #'  )
 #' )
 #'
-#' nycflights13_sql(connections$odbc, schema = "nycflights13")
+#' nycflights13_create_sql(connections$odbc, schema = "nycflights13")
 #' # same as
-#' # nycflights13_sql(connections$rpostgresql, schema = "nycflights13")
+#' # nycflights13_create_sql(connections$rpostgresql, schema = "nycflights13")
 #' # also same as
-#' # nycflights13_sql(connections$rpostgres, schema = "nycflights13")
+#' # nycflights13_create_sql(connections$rpostgres, schema = "nycflights13")
 #' }
-nycflights13_sql <- function(con, schema = "", ...) {
+nycflights13_create_sql <- function(con, schema = "", ...) {
   local_tables <- utils::data(package = "nycflights13")$results[, "Item"]
 
   unique_index <- list(
@@ -144,7 +144,7 @@ nycflights13_sql <- function(con, schema = "", ...) {
 #'
 #' @param location where to store the database
 #' @param ... additional parameters to connect to a database (most are passed on
-#' to [`nycflights13_sql`])
+#' to [`nycflights13_create_sql`])
 #'
 #' @return RSQLiteConnection
 #'
@@ -152,13 +152,38 @@ nycflights13_sql <- function(con, schema = "", ...) {
 #'
 #' @examples
 #' \dontrun{
-#' con <- nycflights13_sqlite()
+#' con <- nycflights13_create_sqlite()
 #' }
-nycflights13_sqlite <- function(location = ":memory:", ...) {
+nycflights13_create_sqlite <- function(location = ":memory:", ...) {
   check_for_pkg("RSQLite")
   sqlite_con <- dbConnect(RSQLite::SQLite(), location)
 
-  sqlite_con <- nycflights13_sql(sqlite_con, schema = "", ...)
+  sqlite_con <- nycflights13_create_sql(sqlite_con, schema = "", ...)
 
   return(invisible(sqlite_con))
 }
+
+#' An SQLite connection to a subset of nycflights13
+#'
+#' Included with `dittodb` is a small subset of [`nycflights13`](nycflights13)
+#' prepopulated into a `sqlite` database.
+#'
+#' This database is helpful for getting to know `dittodb` and running example
+#' code. It contains a small subset of the data in nycflights13: namely only the
+#' flights and planes that had a destination of ORD or MDW in February of 2013.
[…]

### 2020-06-06 tests/testthat/test-a-recording.R

@@ -7,7 +7,7 @@ test_that("We can capture db interactions", {
   expect_null(.dittodb_env$db_path)
 
   start_db_capturing()
-  con <- nycflights13_sqlite()
+  con <- nycflights13_create_sqlite()
 
   # our state has been updated
   expect_identical(.dittodb_env$db_path, file.path(temp_dir, "_memory_"))
@@ -36,7 +36,7 @@ test_that("We can capture db interactions", {
 test_that("We can specify the path when starting capture", {
   new_path <- file.path(temp_dir, "start_capture_path")
   start_db_capturing(new_path)
-  con <- nycflights13_sqlite()
+  con <- nycflights13_create_sqlite()
 
   # our state has been updated
   expect_identical(.dittodb_env$db_path, file.path(new_path, "_memory_"))

### 2020-06-06 tests/testthat/test-verbosity.R

@@ -8,7 +8,7 @@ capture_output({
       dittodb.mock.paths = file.path(temp_dir, "verbosity_mock")
     ), {
       start_db_capturing()
-      con <- nycflights13_sqlite()
+      con <- nycflights13_create_sqlite()
       expect_message(
         dbGetQuery(con, "SELECT * FROM airlines LIMIT 2"),
         paste0(
@@ -44,7 +44,7 @@ capture_output({
     ), {
       expect_message({
           start_db_capturing()
-          con <- nycflights13_sqlite()
+          con <- nycflights13_create_sqlite()
         }, ".*Tracing.*"
       )
       expect_message(

### 2020-06-07 R/nycflights13-sql.R
Documentation cleanup (#110)
* Tabbing in pkgdown!

* Add multiple db backends to readme/vignettes

* Some doc tweaks and adding examples

* Add post-hoc functionality to remove empty TOC items that are generated by tabs generation

@@ -20,38 +20,23 @@
 #' connections <- list(
 #'  odbc = DBI::dbConnect(
 #'   odbc::odbc(),
-#'   Driver   = "PostgreSQL Unicode",
-#'   Server   = "127.0.0.1",
-#'   Database = "postgres",
-#'   UID      = "travis",
-#'   PWD      = "",
-#'   Port     = 5432
+#'   Driver   = "PostgreSQL Unicode"
 #'  ),
 #'  rpostgresql = RPostgreSQL::dbConnect(
-#'   drv      = DBI::dbDriver("PostgreSQL"),
-#'   host     = "127.0.0.1",
-#'   dbname   = "postgres",
-#'   user     = "travis",
-#'   password = "",
-#'   port     = 5432
+#'   drv      = DBI::dbDriver("PostgreSQL")
 #'  ),
 #'  rpostgres = DBI::dbConnect(
-#'   drv      = RPostgres::Postgres(),
-#'   host     = "127.0.0.1",
-#'   dbname   = "postgres",
-#'   user     = "travis",
-#'   password = "",
-#'   port     = 5432
+#'   drv      = RPostgres::Postgres()
 #'  )
 #' )
 #'
-#' nycflights13_sql(connections$odbc, schema = "nycflights13")
+#' nycflights13_create_sql(connections$odbc, schema = "nycflights13")
 #' # same as
-#' # nycflights13_sql(connections$rpostgresql, schema = "nycflights13")
+#' # nycflights13_create_sql(connections$rpostgresql, schema = "nycflights13")
 #' # also same as
-#' # nycflights13_sql(connections$rpostgres, schema = "nycflights13")
+#' # nycflights13_create_sql(connections$rpostgres, schema = "nycflights13")
 #' }
-nycflights13_sql <- function(con, schema = "", ...) {
+nycflights13_create_sql <- function(con, schema = "", ...) {
   local_tables <- utils::data(package = "nycflights13")$results[, "Item"]
 
   unique_index <- list(
@@ -144,7 +129,7 @@ nycflights13_sql <- function(con, schema = "", ...) {
 #'
 #' @param location where to store the database
 #' @param ... additional parameters to connect to a database (most are passed on
-#' to [`nycflights13_sql`])
+#' to [`nycflights13_create_sql`])
 #'
 #' @return RSQLiteConnection
 #'
@@ -152,13 +137,42 @@ nycflights13_sql <- function(con, schema = "", ...) {
 #'
 #' @examples
 #' \dontrun{
[…]

### 2020-06-07 db-setup/create-nycflights-subset.R

@@ -1,0 +1,25 @@
+library(DBI)
+
+nycflights13_sqlite("inst/nycflights.sqlite")
+
+flights_db <- dbConnect(
+  RSQLite::SQLite(), "inst/nycflights.sqlite"
+)
+
+dbSendQuery(flights_db, "DELETE FROM flights WHERE dest NOT IN ('ORD', 'MDW') OR month != 2")
+nrow(dbGetQuery(flights_db, "SELECT * FROM flights"))
+
+dbSendQuery(flights_db, "DELETE FROM weather WHERE month != 2")
+nrow(dbGetQuery(flights_db, "SELECT * FROM weather"))
+
+dbSendQuery(flights_db, "DELETE FROM planes WHERE tailnum IN (SELECT DISTINCT tailnum FROM flights) IS NULL")
+nrow(dbGetQuery(flights_db, "SELECT * FROM planes"))
+
+dbSendQuery(flights_db, "DELETE FROM airlines WHERE carrier NOT IN (SELECT DISTINCT carrier FROM flights)")
+nrow(dbGetQuery(flights_db, "SELECT * FROM airlines"))
+
+dbSendQuery(flights_db, "DELETE FROM airports WHERE faa NOT IN ('ORD', 'MDW', 'LGA', 'JFK', 'EWR')")
+nrow(dbGetQuery(flights_db, "SELECT * FROM airports"))
+
+dbSendQuery(flights_db, "VACUUM")
+dbDisconnect(flights_db)

### 2020-06-07 tests/testthat/test-dbi-sqlite-integration.R

@@ -1,7 +1,7 @@
 context("Test fixture")
 
 # testing against built-in sqlite database
-con <- nycflights13_sqlite()
+con <- nycflights13_create_sqlite()
 
 test_that("The fixture is what we expect", {
   expect_identical(

### 2020-06-07 tests/testthat/test-dbplyr-integration.R

@@ -5,7 +5,7 @@ library(dplyr)
 temp_path <- file.path(temp_dir, "dbplyr_integration")
 
 # testing against built-in sqlite database
-con <- nycflights13_sqlite(temp_path)
+con <- nycflights13_create_sqlite(temp_path)
 
 test_that("The fixture is what we expect", {
   expect_identical(

### 2020-06-07 tests/testthat/test-nycflights13.R

@@ -3,7 +3,7 @@ context("nycflights13 writing functions")
 # sqlite ----
 test_that("nycflights sqlite can be created", {
   # with DBI
-  con <- nycflights13_sqlite()
+  con <- nycflights13_create_sqlite()
   expect_is(con, "SQLiteConnection")
   expect_identical(
     dbListTables(con),
@@ -29,7 +29,7 @@ test_that("odbc", {
 
   test_that("DBI, with a new schema creation and odbc package", {
     expect_message(
-      nycflights13_sql(con_odbc, schema = "new_schema"),
+      nycflights13_create_sql(con_odbc, schema = "new_schema"),
       paste0(c(
         "Creating the testing database from nycflights13",
         "Creating table: airlines",
@@ -45,7 +45,7 @@ test_that("odbc", {
 
   test_that("DBI, with a same schema creation and odbc package", {
     expect_message(
-      nycflights13_sql(con_odbc, schema = "new_schema"),
+      nycflights13_create_sql(con_odbc, schema = "new_schema"),
       "Creating the testing database from nycflights13"
     )
   })
@@ -68,7 +68,7 @@ test_that("RPostgreSQL", {
 
   test_that("DBI, with a new schema creation and rpostgresql package", {
     expect_message(
-      nycflights13_sql(con_rpostgresql, schema = "new_schema_rpostgresql"),
+      nycflights13_create_sql(con_rpostgresql, schema = "new_schema_rpostgresql"),
       paste0(c(
         "Creating the testing database from nycflights13",
         "Creating table: airlines",
@@ -84,7 +84,7 @@ test_that("RPostgreSQL", {
 
   test_that("DBI, with a same schema creation and rpostgresql package", {
     expect_message(
-      nycflights13_sql(con_rpostgresql, schema = "new_schema_rpostgresql"),
+      nycflights13_create_sql(con_rpostgresql, schema = "new_schema_rpostgresql"),
       "Creating the testing database from nycflights13"
     )
   })
@@ -107,7 +107,7 @@ test_that("RPostgres", {
 
   test_that("DBI, with a new schema creation and rpostgres package", {
     expect_message(
-      nycflights13_sql(con_rpostgres, schema = "new_schema"),
+      nycflights13_create_sql(con_rpostgres, schema = "new_schema"),
       paste0(c(
         "Creating the testing database from nycflights13",
         "Creating table: airlines",
[…]

### 2020-07-18 R/connection.R
First pass of changes

@@ -1,9 +1,10 @@
 #' Methods for interacting with DB mocks instead of an actual database
 #'
-#' Various methods (`dbSendQuery`, `dbFetchQuery`) that are mocks of the DBI
-#' methods of the same name. Instead of actually interacting with a database,
-#' they read in mock responses and the code proceeds after that. These aren't
-#' used directly, but are part of how `dittodb` works.
+#' Various methods (`dbSendQuery`, `dbFetchQuery`) that are mocks of the
+#' [DBI](https://CRAN.R-project.org/package=DBI) methods of the same name.
+#' Instead of actually interacting with a database, they read in mock responses
+#' and the code proceeds after that. These aren't used directly, but are part of
+#' how {dittodb} works.
 #'
 #' @param conn a database connection (for dispatch with these methods, it should
 #'   be of class `DBIMockConnection`)

### 2020-07-18 R/mock-db.R

@@ -4,7 +4,7 @@
 #' use fixtures instead of connecting to a real database. Alternatively, you can
 #' start and stop using a mocked database with `start_mock_db()` and
 #' `stop_mock_db()` respectively.to execute the whole thing without needing to
-#' remember to stop the mocking. When testing with `dittodb`, it will look for
+#' remember to stop the mocking. When testing with {dittodb}, it will look for
 #' fixtures in all entries of [`db_mock_paths`].
 #'
 #' You only need to use one approach: either use `start_mock_db()` to start
@@ -17,7 +17,7 @@
 #'
 #' Connections should be made after `start_mock_db()` if you're using that
 #' function or they should be made inside of `with_mock_db()` if you're using
-#' that function because `dittodb` uses the database name (given in `dbname` or
+#' that function because {dittodb} uses the database name (given in `dbname` or
 #' `Database` argument of [`dbConnect`] depending on the driver) to separate
 #' different fixtures.
 #'

### 2020-07-18 R/mock-paths.R

@@ -86,7 +86,7 @@ db_mock_paths <- function(new, last = FALSE) {
 #' Run the DBI queries in an alternate mock directory
 #'
 #' When testing with dittodb, wrap your tests in `with_mock_path({})` to use the
-#' database fixtures located in other directories. `dittodb` will look for
+#' database fixtures located in other directories. {dittodb} will look for
 #' fixtures in the directory specified by the user, which can be a temporary
 #' or permanent location.
 #'

### 2020-07-18 R/nycflights13-sql.R

@@ -150,14 +150,15 @@ nycflights13_create_sqlite <- function(location = ":memory:", ...) {
 
 #' An SQLite connection to a subset of nycflights13
 #'
-#' Included with `dittodb` is a small subset of [`nycflights13`](https://CRAN.R-project.org/package=nycflights13)
+#' Included with {dittodb} is a small subset of
+#' [`nycflights13`](https://CRAN.R-project.org/package=nycflights13)
 #' prepopulated into a `sqlite` database.
 #'
-#' This database is helpful for getting to know `dittodb` and running example
+#' This database is helpful for getting to know {dittodb} and running example
 #' code. It contains a small subset of the data in nycflights13: namely only the
-#' flights and planes that had a destination of ORD or MDW in February of 2013.
-#' The airports table has also been limited to only the New York and Chicago
-#' area airports.
+#' flights and planes that had a destination of ORD or MDW (the codes for the
+#' two major airports in Chicago) in February of 2013. The airports table has
+#' also been limited to only the New York and Chicago area airports.
 #'
 #' @return an RSQLiteConnection
 #'

### 2020-07-18 R/redact.R

@@ -1,7 +1,7 @@
 #' Redact columns from a dataframe with the default redactors
 #'
 #' This function redacts the columns specified in `columns` in the data given in
-#' `data` using dittodb's standard redactors.
+#' `data` using {dittodb}'s standard redactors.
 #'
 #' The column names given in the `columns` argument are treated as regular
 #' expressions, however they always have `^` and `$` added to the beginning and
@@ -21,7 +21,7 @@
 #' @param data a dataframe to redact
 #' @param columns character, the columns to redact
 #' @param ignore.case should case be ignored? (default: `TRUE`)
-#' @param ... additional options to pass on to `grep` when matching the column
+#' @param ... additional options to pass on to `grep()` when matching the column
 #' names
 #'
 #' @return data, with the columns specified in `columns` duly redacted

### 2020-07-18 R/utils.R

@@ -1,8 +1,5 @@
-#' @importFrom utils installed.packages
 check_for_pkg <- function(package) {
-  installed_packages <- rownames(installed.packages())
-
-  if (!package %in% installed_packages) {
+  if (!requireNamespace(package)) {
     # TODO: also allow warnings?
     stop(
       "The package ",
@@ -94,14 +91,14 @@ ignore_quotes <- function(statement) {
 
 #' Set dittodb's debug level
 #'
-#' It can be helpful to see what's going on by increasing `dittodb`'s verbosity
+#' It can be helpful to see what's going on by increasing {dittodb}'s verbosity
 #' which will show what's going on under the hood (e.g. what queries are being
 #' requested, from where).
 #'
 #' The `level` argument is a numeric, where 0 is the default and (relatively)
-#' silent. The higher the level, the more verbose `dittodb` will be.
+#' silent. The higher the level, the more verbose {dittodb} will be.
 #'
-#' Currently, `dittodb` only has one level of debugging (any value 1 or
+#' Currently, {dittodb} only has one level of debugging (any value 1 or
 #' greater), but more might be used in the future.
 #'
 #' @param level a numeric, the level to set to (e.g. 1)
@@ -148,7 +145,7 @@ get_type <- function(statement) return(strsplit(statement, " ")[[1]][1])
 #' Sanitize Table id
 #'
 #' Tables are identified and specified with a large number of ways across
-#' drivers. For the purposes of `dittodb`, the details are less important since
+#' drivers. For the purposes of {dittodb}, the details are less important since
 #' we almost always just want a flat representation (_ie_ for filenames). This
 #' takes the various formats and returns a string with various elements
 #' separated by dots.

### 2020-07-19 R/capture-requests.R
CRAN comments (#123)

@@ -33,7 +33,7 @@
 #' @return `NULL` (invisibily)
 #'
 #' @examples
-#' \dontrun{
+#' \donttest{
 #' # Temporary files for examples
 #' nycflights_path <- tempfile()
 #'
@@ -275,12 +275,6 @@ dbColumnInfoTrace <- quote({
   path <- make_path(.dittodb_env$db_path, "columnInfo", hash)
   dput(thing, path, control = c("all", "hexNumeric"))
 })
-
-#' an environment for dittodb storing state
-#'
-#' @export
-#' @keywords internal
-.dittodb_env <- new.env(parent = emptyenv())
 
 #' @rdname capture_requests
 #' @export

### 2020-07-19 R/dittodb-env.R

@@ -1,0 +1,12 @@
+#' @include mock-paths.R
+NULL
+
+#' an environment for dittodb storing state
+#'
+#' @export
+#' @keywords internal
+.dittodb_env <- new.env(parent = emptyenv())
+
+# Set the default mock paths, use both "." and "tests/testthat/" in case they
+# are different
+set_default_db_mock_paths()

### 2020-07-19 R/mock-db.R

@@ -4,7 +4,7 @@
 #' use fixtures instead of connecting to a real database. Alternatively, you can
 #' start and stop using a mocked database with `start_mock_db()` and
 #' `stop_mock_db()` respectively.to execute the whole thing without needing to
-#' remember to stop the mocking. When testing with `dittodb`, it will look for
+#' remember to stop the mocking. When testing with {dittodb}, it will look for
 #' fixtures in all entries of [`db_mock_paths`].
 #'
 #' You only need to use one approach: either use `start_mock_db()` to start
@@ -17,7 +17,7 @@
 #'
 #' Connections should be made after `start_mock_db()` if you're using that
 #' function or they should be made inside of `with_mock_db()` if you're using
-#' that function because `dittodb` uses the database name (given in `dbname` or
+#' that function because {dittodb} uses the database name (given in `dbname` or
 #' `Database` argument of [`dbConnect`] depending on the driver) to separate
 #' different fixtures.
 #'
@@ -30,7 +30,6 @@
 #' @name mockdb
 #'
 #' @examples
-#' \dontrun{
 #' # Add the mocks included with dittodb to the db_mock_paths to use them below
 #' db_mock_paths(system.file("nycflight_mocks", package = "dittodb"), last = TRUE)
 #'
@@ -41,42 +40,40 @@
 #'     dbname = "nycflights"
 #'   )
 #'
-#'   test_that("We get one airline", {
+#'   testthat::test_that("We get one airline", {
 #'     one_airline <- dbGetQuery(
 #'       con,
 #'       "SELECT carrier, name FROM airlines LIMIT 1"
 #'     )
-#'     expect_is(one_airline, "data.frame")
-#'     expect_equal(nrow(one_airline), 1)
-#'     expect_equal(one_airline$carrier, "9E")
-#'     expect_equal(one_airline$name, "Endeavor Air Inc.")
+#'     testthat::expect_is(one_airline, "data.frame")
+#'     testthat::expect_equal(nrow(one_airline), 1)
+#'     testthat::expect_equal(one_airline$carrier, "9E")
+#'     testthat::expect_equal(one_airline$name, "Endeavor Air Inc.")
 #'   })
+#'
+#'   dbDisconnect(con)
 #' })
 #'
[…]

### 2020-07-19 R/mock-paths.R

@@ -15,9 +15,11 @@
 #' want to set the `last` argument to `TRUE` if you want to read from a
 #' directory but don't want to write to it.
 #'
-#' For finer-grained control, or to completely override the default behavior
-#' of searching in the current working directory, you can set the option
-#' "dittodb.mock.paths" directly.
+#' For finer-grained control, or to completely override the defaults or any
+#' additions made by calls to `db_mock_paths(...)`, you can set the option
+#' "dittodb.mock.paths". If the option "dittodb.mock.paths" is set it will be
+#' used instead of any paths set with `db_mock_paths(...)` or even inside of
+#' `with_mock_path()`
 #'
 #' This function is similar to `.mockPaths()` from
 #' [httptest](https://CRAN.R-project.org/package=httptest)
@@ -29,12 +31,14 @@
 #' to the default.
 #' @param last a logical, should the new path given be added to the end of the
 #' list of paths? (default: `FALSE`)
+#' @param replace logical, should the path replace the current mock paths
+#' (`TRUE`) or should they be appended (to the beginning) of the current mock
+#' paths (default, `FALSE`)
 #'
 #' @return If `new` is omitted, the function returns the current search paths, a
 #' character vector. If `new` is provided, the updated value will be returned
 #' invisibly.
 #' @examples
-#' \dontrun{
 #' # reset mock paths to default
 #' db_mock_paths(NULL)
 #'
@@ -45,33 +49,54 @@
 #' identical(db_mock_paths(), c("tests/testthat/", "."))
 #' db_mock_paths("/var/somewhere/else", last = TRUE)
 #' identical(db_mock_paths(), c("tests/testthat/", ".", "/var/somewhere/else"))
-#' }
 #' @name mockPaths
 #' @export
-db_mock_paths <- function(new, last = FALSE) {
-  # use both "." and testthat::test_path(".") in case they are different
-  def <- unique(c("tests/testthat/", "."))
-
-  current <- getOption("dittodb.mock.paths", default = def)
+db_mock_paths <- function(new, last = FALSE, replace = FALSE) {
+  # We're calling the function to get the list of paths
   if (missing(new)) {
-    ## We're calling the function to get the list of paths
-    return(current)
-  } else if (is.null(new)) {
-    ## We're calling the function to reset to the default
-    options(dittodb.mock.paths = new)
-  } else {
[…]

### 2020-07-19 R/utils.R

@@ -1,8 +1,5 @@
-#' @importFrom utils installed.packages
 check_for_pkg <- function(package) {
-  installed_packages <- rownames(installed.packages())
-
-  if (!package %in% installed_packages) {
+  if (!requireNamespace(package, quietly = TRUE)) {
     # TODO: also allow warnings?
     stop(
       "The package ",
@@ -92,16 +89,18 @@ ignore_quotes <- function(statement) {
   return(gsub("(`|\"|')", "`", statement))
 }
 
-#' Set dittodb's debug level
+#' Set {dittodb}'s debug level
 #'
-#' It can be helpful to see what's going on by increasing `dittodb`'s verbosity
+#' It can be helpful to see what's going on by increasing {dittodb}'s verbosity
 #' which will show what's going on under the hood (e.g. what queries are being
-#' requested, from where).
+#' requested, from where). This sets the option `dittodb.debug` to the value
+#' given in the `level` argument. The option can be set directly with
+#' `options(dittodb.debug = n)` as well.
 #'
 #' The `level` argument is a numeric, where 0 is the default and (relatively)
-#' silent. The higher the level, the more verbose `dittodb` will be.
+#' silent. The higher the level, the more verbose {dittodb} will be.
 #'
-#' Currently, `dittodb` only has one level of debugging (any value 1 or
+#' Currently, {dittodb} only has one level of debugging (any value 1 or
 #' greater), but more might be used in the future.
 #'
 #' @param level a numeric, the level to set to (e.g. 1)
@@ -113,7 +112,7 @@ ignore_quotes <- function(statement) {
 #' set_dittodb_debug_level(1)
 #' set_dittodb_debug_level(0)
 set_dittodb_debug_level <- function(level) {
-  stopifnot(is.numeric(level))
+  stopifnot(is.numeric(level) || is.null(level))
   options("dittodb.debug" = level)
 
   return(invisible(level))
@@ -148,7 +147,7 @@ get_type <- function(statement) return(strsplit(statement, " ")[[1]][1])
 #' Sanitize Table id
 #'
 #' Tables are identified and specified with a large number of ways across
-#' drivers. For the purposes of `dittodb`, the details are less important since
+#' drivers. For the purposes of {dittodb}, the details are less important since
 #' we almost always just want a flat representation (_ie_ for filenames). This
 #' takes the various formats and returns a string with various elements
 #' separated by dots.

### 2020-07-19 tests/testthat/test-mock-paths.R

@@ -28,6 +28,15 @@ withr::with_options(
     test_that("dittodb.mock.paths is used", {
       expect_identical(db_mock_paths(), "new_one")
     })
+  })
+
+with_mock_path(
+  c("new_one"),
+  replace = TRUE,
+  {
+    test_that("the one mockpath is used", {
+      expect_identical(db_mock_paths(), "new_one")
+    })
 
     test_that("and we can unset", {
       db_mock_paths(NULL)
@@ -44,6 +53,13 @@ withr::with_options(
     test_that("and we can add to the end", {
       db_mock_paths("end", last = TRUE)
       expect_identical(db_mock_paths(), c("tests/testthat/", ".", "end"))
+      # cleanup
+      db_mock_paths(NULL)
+    })
+
+    test_that("and we can replace", {
+      db_mock_paths("replace", replace = TRUE)
+      expect_identical(db_mock_paths(), c("replace"))
       # cleanup
       db_mock_paths(NULL)
     })

### 2020-10-01 R/dbQueries-Results.R
A bit more cleanup

@@ -22,24 +22,6 @@ setClass("DBIMockResult",
          contains = "DBIResult"
 )
 
-setValidity("DBIMockResult", function(res) {
-  path <- make_path(res@path, res@type, res@hash)
-  tryCatch(
-    find_file(path),
-    error = function(e) {
-      stop(
-        "Fixture: ",
-        path,
-        "\n",
-        clean_statement(res@statement),
-        call. = FALSE
-      )
-    }
-  )
-
-  return(TRUE)
-})
-
 #' @rdname mock-db-methods
 #' @importFrom methods setMethod new
 #' @export
@@ -56,7 +38,13 @@ setMethod(
 
     # TDOO: if we are in expect_sql, then we should emit an error (or warning?) with SQL here
     if (is_expecting()) {
-      stop(clean_statement(statement), call. = FALSE)
+      stop(
+        "Fixture: ",
+        make_path(conn@path, get_type(statement), hash(statement)),
+        "\n",
+        clean_statement(statement),
+        call. = FALSE
+      )
     }
 
     return(new(

### 2020-10-01 R/expect-sql.R

@@ -12,8 +12,22 @@
 #'
 #' @export
 #'
+#' @examples
+#' if (check_for_pkg("RSQLite", message)) {
+#'   with_mock_db({
+#'     con <- dbConnect(RSQLite::SQLite(), dbname = "not_a_db")
+#'
+#'     expect_sql(
+#'       dbGetQuery(con, "SELECT carrier, name FROM airlines LIMIT 3"),
+#'       "SELECT carrier, name FROM airlines LIMIT 3"
+#'     )
+#'   })
+#' }
 expect_sql <- function(object,
                        regexp = NULL,
                        ...) {
-  expect_error(object = object, regexp = regexp, ...)
+  .dittodb_env$expecting <- TRUE
+  on.exit(.dittodb_env$expecting <- FALSE)
+
+  testthat::expect_error(object = object, regexp = regexp, ...)
 }

### 2020-10-08 .github/r-hub-checks.R
Prepare for new dbplyr subquery names

@@ -4,6 +4,8 @@ cran_plat <- plat[!is.na(plat$`cran-name`), ]
 rhub_plat <- cran_plat[!grepl("debian|fedora", cran_plat$name), ]
 debfed_plat <- cran_plat[grepl("debian|fedora", cran_plat$name), ]
 
+devtools::check_win_devel()
+devtools::check_win_release()
 
 rhub::check_for_cran()
 

### 2020-10-08 R/utils.R

@@ -108,6 +108,11 @@ ignore_dbplyr_unique_names <- function(statement) {
     "`removed_unique_dplyr_name`",
     statement
   )
+  statement <- gsub(
+    "`q[[:digit:]]+`",
+    "`removed_unique_dplyr_name`",
+    statement
+  )
   return(statement)
 }
 

### 2020-10-08 tests/testthat/test-utils.R

@@ -43,6 +43,7 @@ test_that("path sanitization", {
 test_that("we can remove the unique dbplyr names", {
   with_unique <- "SELECT *\nFROM `airlines` AS `zzz26`"
   with_dbplyr <- "SELECT *\nFROM `airlines` AS `dbplyr_009`"
+  with_dbplyr2 <- "SELECT *\nFROM `airlines` AS `q01`"
   no_unique <- "SELECT *\nFROM `airlines` AS `my_special_airlines_table`"
   with_quotes <- "SELECT *\nFROM \"airlines\" AS \"zzz16\""
   with_unique_long <- "SELECT *\nFROM `airlines` AS `zzz26666`"
@@ -52,6 +53,7 @@ test_that("we can remove the unique dbplyr names", {
 
   expect_identical(ignore_dbplyr_unique_names(with_unique), expected)
   expect_identical(ignore_dbplyr_unique_names(with_dbplyr), expected)
+  expect_identical(ignore_dbplyr_unique_names(with_dbplyr2), expected)
   expect_identical(ignore_dbplyr_unique_names(no_unique), no_unique)
   expect_identical(ignore_dbplyr_unique_names(with_unique_long), expected)
   expect_identical(

### 2020-10-08 vignettes/travelling-old/SELECT-cb2164.R

@@ -1,15 +1,15 @@
 structure(list(tailnum = c("N912XJ", "N645JB", "N904WN", "N3BWAA", 
-"N3CJAA", "N14972", "N667UA", "N521JB", "N998AT", "N16559", "N14186", 
-"N16170", "N789JB", "N593JB", "N409WN", "N11535", "N505AA", "N8928A", 
-"N3DPAA", "N34222", "N639VA", "N480AA", "N77518", "N511MQ", "N697DL", 
-"N87527", "N652SW", "N651JB", "N640AA", "N304DQ", "N988DL", "N643JB", 
+"N3CJAA", "N14972", "N667UA", "N998AT", "N521JB", "N16559", "N14186", 
+"N16170", "N789JB", "N409WN", "N593JB", "N11535", "N505AA", "N8928A", 
+"N3DPAA", "N34222", "N639VA", "N480AA", "N511MQ", "N77518", "N697DL", 
+"N87527", "N652SW", "N651JB", "N640AA", "N304DQ", "N643JB", "N988DL", 
 "N231JB", "N14542", "N531JB", "N14573", "N76519", "N13161", "N567UA", 
 "N201LV", "N27962", "N198JB", "N520MQ", "N689MQ", "N369NW", "N8432A", 
-"N14902", "N8EGMQ", "N3FJAA", "N336NB", "N905DL", "N12136", "N628VA", 
-"N550WN", "N844VA", "N353SW", "N738US", "N371NB", "N431WN", "N11206", 
+"N14902", "N8EGMQ", "N336NB", "N3FJAA", "N905DL", "N628VA", "N12136", 
+"N550WN", "N353SW", "N844VA", "N738US", "N371NB", "N431WN", "N11206", 
 "N412WN", "N832UA", "N14993", "N495UA", "N3759", "N314US", "N14231", 
 "N176DN", "N363NB", "N3AHAA", "N5DMAA", "N764US", "N802MQ", "N33209", 
-"N38451", "N14219", "N320US", "N8903A", "N682MQ", "N672DL", "N3FCAA", 
+"N38451", "N14219", "N320US", "N8903A", "N3FCAA", "N682MQ", "N672DL", 
 "N173US", "N691CA", "N33103", "N210WN", "N8877A", "N638JB", "N558UW", 
 "N820AS", "N479UA", "N180US", "N334JB", "N33292", "N513UA", "N775JB", 
[…]

### 2020-10-08 vignettes/travelling/SELECT-526b8c.R

@@ -1,0 +1,152 @@
+structure(list(oid = c(16L, 17L, 18L, 19L, 20L, 21L, 22L, 23L, 
+24L, 25L, 26L, 27L, 28L, 29L, 30L, 71L, 75L, 81L, 83L, 114L, 
+142L, 194L, 3361L, 3402L, 5017L, 32L, 5069L, 600L, 601L, 602L, 
+603L, 604L, 628L, 700L, 701L, 705L, 718L, 790L, 829L, 869L, 650L, 
+774L, 1033L, 1042L, 1043L, 1082L, 1083L, 1114L, 1184L, 1186L, 
+1266L, 1560L, 1562L, 1700L, 1790L, 2202L, 2203L, 2204L, 2205L, 
+4191L, 2206L, 4096L, 4089L, 2950L, 3220L, 3614L, 3642L, 3615L, 
+3734L, 3769L, 3802L, 4072L, 2970L, 5038L, 3904L, 3906L, 3908L, 
+3910L, 3912L, 3926L, 2249L, 2287L, 2275L, 2276L, 2277L, 2278L, 
+2279L, 3838L, 2280L, 2281L, 2283L, 2776L, 3500L, 3115L, 325L, 
+3310L, 269L, 3831L, 5077L, 5078L, 5079L, 5080L, 1000L, 1001L, 
+1002L, 1003L, 1016L, 1005L, 1006L, 1007L, 1008L, 1009L, 1028L, 
+1010L, 1011L, 1012L, 1013L, 199L, 143L, 271L, 1017L, 1018L, 1019L, 
+1020L, 1027L, 629L, 1021L, 1022L, 719L, 791L, 1040L, 1041L, 651L, 
+775L, 1034L, 1014L, 1015L, 1182L, 1183L, 1115L, 1185L, 1187L, 
+1270L, 1561L, 1563L, 1231L, 2201L, 2207L, 2208L, 2209L, 2210L, 
+4192L, 2211L, 4097L, 4090L, 2951L, 3221L, 3643L, 3644L, 3645L, 
+3735L, 3770L, 3807L, 4073L, 2949L, 5039L, 3905L, 3907L, 3909L, 
+3911L, 3913L, 3927L, 1263L, 12000L, 12001L, 12002L, 12003L, 12004L, 
+12005L, 12006L, 12007L, 12008L, 12009L, 12010L, 12011L, 12012L, 
[…]

### 2020-10-08 vignettes/travelling/SELECT-90cd6a.R

@@ -1,0 +1,8 @@
+structure(list(year = integer(0), month = integer(0), day = integer(0), 
+    dep_time = integer(0), sched_dep_time = integer(0), dep_delay = numeric(0), 
+    arr_time = integer(0), sched_arr_time = integer(0), arr_delay = numeric(0), 
+    carrier = character(0), flight = integer(0), tailnum = character(0), 
+    origin = character(0), dest = character(0), air_time = numeric(0), 
+    distance = numeric(0), hour = numeric(0), minute = numeric(0), 
+    time_hour = structure(numeric(0), class = c("POSIXct", "POSIXt"
+    ))), class = "data.frame", row.names = c(NA, 0L))

### 2021-10-15 tests/testthat/test-dbi-generic-integration.R
add quoting for postgres, some CI fixes

@@ -42,9 +42,10 @@ db_pkgs <- list(
   ))
 )
 
+db_pkgs <- db_pkgs["RPostgreSQL"]
+
 # The lintr complains about cyclomatic complexity here because of the stacked
 # calls needed for test_that + dittodb + database calls.
-# nolint start
 for (pkg in names(db_pkgs)) {
   test_that(glue("Integration tests for {pkg}"), {
     skip_env(pkg)
@@ -70,6 +71,21 @@ for (pkg in names(db_pkgs)) {
     } else {
       airlines_table <- paste(schema, "airlines", sep = ".")
       flights_table <- paste(schema, "flights", sep = ".")
+    }
+
+    # slightly different ways to refer to tables/schemas
+    if (pkg == "RMariaDB") {
+      flights_table_obj <- "flights"
+      airlines_table_obj <- "airlines"
+      doesnotexist_table_obj <- "doesnotexist"
+    } else if (pkg == "RPostgreSQL") {
+      flights_table_obj <- c(schema = schema, table = "flights")
+      airlines_table_obj <- c(schema = schema, table = "airlines")
+      doesnotexist_table_obj <- c(schema = schema, table = "doesnotexist")
+    } else if (pkg %in% c("odbc", "RPostgres")) {
+      flights_table_obj <- Id(schema = schema, table = "flights")
+      airlines_table_obj <- Id(schema = schema, table = "airlines")
+      doesnotexist_table_obj <- c(schema = schema, table = "doesnotexist")
     }
 
     test_that(glue("The fixture is what we expect: {pkg}"), {
@@ -112,38 +128,12 @@ for (pkg in names(db_pkgs)) {
       tables <- dbListTables(con)
 
       # dbListFields ====
-      # dbListFields is ever so slightly different for each
-      if (pkg == "RMariaDB") {
-        fields_flights <- dbListFields(con, "flights")
-      } else if (pkg == "odbc") {
-        fields_flights <- dbListFields(
-          con,
-          Id(schema = schema, table = "flights")
-        )
-      } else if (pkg == "RPostgreSQL") {
-        fields_flights <- dbListFields(con, c(schema, "flights"))
-      } else if (pkg == "RPostgres") {
-        fields_flights <- dbListFields(
-          con,
-          Id(schema = schema, table = "flights")
-        )
-      }
+      # dbListFields is ever so slightly different for RPostgresql
+      fields_flights <- dbListFields(con, flights_table_obj)
+
 
       # dbReadTable ====
-      if (pkg == "RMariaDB") {
[…]

### 2021-10-15 tests/testthat/test-dbplyr-integration.R

@@ -75,7 +75,11 @@ with_mock_db({
   # our flights table
   expect_warning(
     flights_db <- tbl(con, "flights"),
-    if (packageVersion("dbplyr") > "1.99") NA else "dbFetch `n` is ignored while mocking databases\\."
+    if (packageVersion("dbplyr") > "1.99") {
+      NA
+    } else {
+      "dbFetch `n` is ignored while mocking databases\\."
+    }
   )
 
   test_that("We can select columns", {

### 2021-11-02 R/capture-requests.R
Don't error with transactions (#151)

@@ -134,6 +134,11 @@ start_db_capturing <- function(path, redact_columns = NULL) {
     exit = dbColumnInfoTrace
   ))
 
+  quietly(trace_dbi(
+    "dbGetRowsAffected",
+    exit = dbGetRowsAffectedTrace
+  ))
+
   # TODO: for RPostgreSQL to work, we need to prevent RPostgreSQL's
   # `postgresqlCloseConnection` from calling `dbListResults` which over-writes
   # our fixture
@@ -183,7 +188,13 @@ dbConnectTrace <- quote({
 })
 
 dbSendQueryTrace <- quote({
-  if (dittodb_debug_level(1)) {
+  if (dittodb_debug_level(2)) {
+    message(
+      "The statement: \n", statement,
+      "\nwhich has been cleaned to: \n", clean_statement(statement),
+      "\nis being hased to: ", hash(statement)
+    )
+  } else if (dittodb_debug_level(1)) {
     message(
       "The statement: \n", statement,
       "\nis being hased to: ", hash(statement)
@@ -238,7 +249,7 @@ dbGetInfoConTrace <- quote({
 dbGetInfoResultTrace <- quote({
   thing <- returnValue()
   # TODO: would this be better if we traced the methods individually?
-  if (inherits(dbObj, c("MariaDBResult", "PqResult"))) {
+  if (inherits(dbObj, c("MariaDBResult", "PqResult", "SQLiteResult"))) {
     hash <- hash(dbObj@sql)
   } else if (inherits(dbObj, "OdbcResult")) {
     hash <- hash(dbObj@statement)
@@ -261,13 +272,14 @@ dbGetInfoPsqlresultTrace <- quote({
   }
 })
 
+# TODO: rationalize these so that they are the same for any list/scalar?
 dbColumnInfoTrace <- quote({
   thing <- returnValue()
   # TODO: would this be better if we traced the methods using signature?
   if (inherits(res, "PostgreSQLResult")) {
     result_info <- RPostgreSQL::postgresqlResultInfo(res)
     hash <- hash(result_info$statement)
-  } else if (inherits(res, c("MariaDBResult", "PqResult"))) {
+  } else if (inherits(res, c("MariaDBResult", "PqResult", "SQLiteResult"))) {
     hash <- hash(res@sql)
   } else if (inherits(res, "OdbcResult")) {
     hash <- hash(res@statement)
@@ -278,12 +290,30 @@ dbColumnInfoTrace <- quote({
[…]

### 2021-11-02 R/dbQueries-Results.R

@@ -24,7 +24,13 @@ setClass("DBIMockResult",
 
 db_send_query <- function(conn, statement, ...) {
   # create a new mock result with the type and a hash of the statement.
-  if (dittodb_debug_level(1)) {
+  if (dittodb_debug_level(2)) {
+    message(
+      "Sending a query for the statement: \n", statement,
+      "\nwhich has been cleaned to: \n", clean_statement(statement),
+      "\nis being hased to: ", hash(statement)
+    )
+  } else if (dittodb_debug_level(1)) {
     message(
       "Sending a query for the statement: \n", statement,
       "\nis being hased to: ", hash(statement)
@@ -59,7 +65,12 @@ setMethod("dbSendQuery", signature("DBIMockConnection", "character"), db_send_qu
 #' @rdname mock-db-methods
 #' @importFrom methods setMethod new
 #' @export
-setMethod("dbSendQuery", signature("DBIMockConnection", "sql"), db_send_query)
+setMethod("dbSendQuery", signature("DBIMockConnection", "SQL"), db_send_query)
+
+#' @rdname mock-db-methods
+#' @importFrom methods setMethod new
+#' @export
+setMethod("dbSendStatement", signature("DBIMockConnection", "character"), db_send_query)
 
 mock_fetch <- function(res, n, ...) {
   if (n != -1) {
@@ -77,7 +88,7 @@ setMethod("dbFetch", signature("DBIMockResult", "ANY"), mock_fetch)
 # use only fetch, so we need to mock both. The complication is that DBI's
 # dbFetch by default simply calls fetch which might lead to duplication
 
-# the @alaises shouldn't be necesary here, but neverthless is.
+# the @alaises shouldn't be necesary here, but nevertheless is.
 #' @rdname mock-db-methods
 #' @aliases fetch,DBIMockResult-method
 #' @export
@@ -118,5 +129,16 @@ setMethod(
     # https://github.com/tomoakin/RPostgreSQL/blob/master/RPostgreSQL/R/PostgreSQLSupport.R#L266 #nolint
     res <- dbSendQuery(conn, statement, ...)
     return(mock_fetch(res, -1))
+  }
+)
+
+#' @rdname mock-db-methods
+#' @export
+setMethod(
+  "dbGetRowsAffected",
+  "DBIMockResult",
+  function(res, ...) {
+    path <- make_path(res@path, "dbGetRowsAffected", res@hash)
+    return(read_file(find_file(path)))
   }
 )

### 2021-11-02 R/transactions.R

@@ -1,0 +1,26 @@
+#' @rdname mock-db-methods
+#' @export
+setMethod(
+  "dbBegin",
+  "DBIMockConnection",
+  function(conn, ..., name = NULL) {
+    return(invisible(TRUE))
+  })
+
+#' @rdname mock-db-methods
+#' @export
+setMethod(
+  "dbCommit",
+  "DBIMockConnection",
+  function(conn, ..., name = NULL) {
+    return(invisible(TRUE))
+  })
+
+#' @rdname mock-db-methods
+#' @export
+setMethod(
+  "dbRollback",
+  "DBIMockConnection",
+  function(conn, ..., name = NULL) {
+    return(invisible(TRUE))
+  })

### 2021-11-02 R/utils.R

@@ -117,7 +117,14 @@ ignore_dbplyr_unique_names <- function(statement) {
 }
 
 ignore_quotes <- function(statement) {
-  return(gsub("(`|\"|')", "`", statement))
+  # remove all the quotes
+  # sometimes E' has a space before it, so add that in (not sure if this is from
+  # dbplyr or RPostgres)
+  # TODO: should we clean up white space separately?
+  statement <- gsub("(`|\"|'| ?E')", "`", statement)
+  # how could we even know how many \s will show up?
+  statement <- gsub("\\\\+", "\\\\", statement)
+  return(statement)
 }
 
 #' Set {dittodb}'s debug level
@@ -202,7 +209,7 @@ sanitize_table_id <- function(id, ...) {
     id <- c(dots, id)
   }
 
-  return(paste0(id, collapse = "."))
+  return(paste0(gsub("\"", "", id), collapse = "."))
 }
 
 # borrowed from Neal borrowing from Hadley

### 2021-11-02 tests/testthat/test-dbi-generic-integration.R

@@ -122,13 +122,25 @@ for (pkg in names(db_pkgs)) {
       dbGetQuery(con, glue("SELECT * FROM {airlines_table} LIMIT 2"))
       dbGetQuery(con, glue("SELECT * FROM {airlines_table} LIMIT 1"))
 
+      # dbGetQuery + regex ====
+      if (pkg == "RMariaDB") {
+        dot_name_regex <- "`name` REGEXP '\\.'"
+      } else if (pkg == "RPostgres") {
+        dot_name_regex <- "\"name\" ~ E'\\.'"
+      } else if (pkg %in% c("odbc", "RPostgreSQL")) {
+        dot_name_regex <- "\"name\" ~ '\\.'"
+      }
+      dot_names <- dbGetQuery(
+        con,
+        glue("SELECT * FROM {airlines_table} WHERE ({dot_name_regex}) LIMIT 3")
+      )
+
       # dbListTables ====
       tables <- dbListTables(con)
 
       # dbListFields ====
       # dbListFields is ever so slightly different for RPostgresql
       fields_flights <- dbListFields(con, flights_table_obj)
-
 
       # dbReadTable ====
       airlines_expected <- dbReadTable(con, airlines_table_obj)
@@ -149,7 +161,7 @@ for (pkg in names(db_pkgs)) {
       table_exists <- dbExistsTable(con, airlines_table_obj)
       table_does_not_exist <- dbExistsTable(con, doesnotexist_table_obj)
 
-      # capturing with dplyr + a string ----
+      # dplyr + a string ====
       require(dbplyr, quietly = TRUE)
       require(dplyr,  quietly = TRUE, warn.conflicts = FALSE)
       if (pkg == "RPostgreSQL") {
@@ -162,6 +174,39 @@ for (pkg in names(db_pkgs)) {
           filter(dest == "ORD") %>%
           collect()
       }
+
+      # dplyr + a regex ====
+      if (pkg == "RPostgreSQL") {
+        # The _one_ place where RPostgreSQL needs `Id()` and not `c(schema, table)`
+        dot_names_dplyr <- tbl(con, Id(airlines_table_obj)) %>%
+          filter(str_detect(name, "\\.")) %>%
+          collect()
+      } else {
+        dot_names_dplyr <- tbl(con, airlines_table_obj) %>%
+          filter(str_detect(name, "\\.")) %>%
+          collect()
+      }
+
+      # joins with df ====
+      local_df <- nycflights13::airlines
[…]

### 2021-11-02 tests/testthat/test-quote.R

@@ -16,5 +16,5 @@ test_that("quoting works", {
   expect_identical(dbQuoteIdentifier(con_rpostgres, "foo"), SQL('"foo"'))
   # However, MariaDB is slightly different (we haven't redefined it, since it
   # doesn't communicate with the DB first)
-  expect_identical(dbQuoteIdentifier(con_mockmaria, "foo"), SQL('`foo`'))
+  expect_identical(dbQuoteIdentifier(con_mockmaria, "foo"), SQL("`foo`"))
 })

### 2021-11-02 tests/testthat/test-transactions.R

@@ -1,0 +1,14 @@
+test_that("transactions", {
+  con_mockmaria <- con_rpostgres <- list()
+  class(con_mockmaria) <- "DBIMockMariaDBConnection"
+  class(con_rpostgres) <- "DBIMockRPostgresConnection"
+
+  # these are all currently no-ops
+  expect_true(dbBegin(con_mockmaria))
+  expect_true(dbCommit(con_mockmaria))
+  expect_true(dbRollback(con_mockmaria))
+
+  expect_true(dbBegin(con_rpostgres))
+  expect_true(dbCommit(con_rpostgres))
+  expect_true(dbRollback(con_rpostgres))
+})

### 2021-11-24 R/mock-db.R
move testthat from Imports to Suggests

@@ -25,7 +25,6 @@
 #' @param expr the expression to execute
 #'
 #' @return nothing
-#' @importFrom testthat with_mock
 #' @export
 #'
 #' @name mockdb

### 2023-04-04 R/utils.R
Allow an ephemeral RSQLite connection

@@ -39,20 +39,23 @@ check_for_pkg <- function(package, func = stop) {
 #' Get the `dbname` from a connection call
 #'
 #' @param dots from the argument being passed to the connection
+#' @param drv from the argument being passed to the connection
 #'
 #' @return the name, sanitized if needed
 #'
 #' @keywords internal
 #'
 #' @export
-get_dbname <- function(dots) {
+get_dbname <- function(dots, drv = NULL) {
   # look through dots to grab either dbname or the first unnammed argument
   named_dbname <- !is.null(dots$dbname) && dots$dbname != ""
+  dbname_is_empty <- is.null(dots$dbname) || dots$dbname == ""
   named_database <- !is.null(dots$Database) && dots$Database != ""
   named_dsn <- !is.null(dots$dsn) && dots$dsn != ""
   unnamed_dbname <- length(dots) > 0 &&
     (is.null(names(dots[1])) || names(dots[1]) == "")
-  # if there is no name, or it's empty
+  drv_is_SQLite <- !is.null(drv) && inherits(drv, "SQLiteDriver")
+
   if (named_dbname) {
     path <- dots$dbname
   } else if (named_database) {
@@ -61,7 +64,11 @@ get_dbname <- function(dots) {
     path <- dots$dsn
   } else if (unnamed_dbname) {
     path <- dots[[1]]
+  } else if (drv_is_SQLite && dbname_is_empty) {
+    # RSQLite will create an ephemeral connection here
+    path <- "ephemeral_sqlite"
   } else {
+    # if there is no name, or it's empty
     stop("There was no dbname, so I don't know where to look for mocks.")
   }
   return(db_path_sanitize(path))

### 2023-04-04 tests/testthat/test-connection.R

@@ -7,12 +7,32 @@ test_that("Error handling", {
   )
 })
 
+test_that("And that RSQLite, without anything captures", {
+  capture_db_requests({
+    con <- dbConnect(RSQLite::SQLite())
+    expect_identical(.dittodb_env$db_path, file.path(temp_dir, "ephemeral_sqlite"))
+    dbDisconnect(con)
+  },
+  path = temp_dir
+  )
+})
+
+
 with_mock_db({
   test_that("Our connection is a mock connection", {
     # ":memory:" is non-portable, so using something close, but portable
     con <- dbConnect(RSQLite::SQLite(), "memory")
     expect_s4_class(con, "DBIMockConnection")
     expect_identical(con@path, "memory")
+    expect_identical(con@original_class, "SQLiteConnection")
+
+    dbDisconnect(con)
+  })
+
+  test_that("And that RSQLite, without anything works", {
+    con <- dbConnect(RSQLite::SQLite())
+    expect_s4_class(con, "DBIMockConnection")
+    # expect_identical(con@path, "memory")
     expect_identical(con@original_class, "SQLiteConnection")
 
     dbDisconnect(con)

### 2024-04-09 R/capture-requests.R
A bit of cleanup

@@ -435,7 +435,7 @@ get_redactor <- function() {
   return(NULL)
 }
 
-#' Check dittodb environment path
+#' Check for dittodb environment path
 #'
 #' This function should generally not be used, but must be exported for the
 #' query recording function to work properly
@@ -443,6 +443,7 @@ get_redactor <- function() {
 #' @param .dittodb_env Environment object
 #'
 #' @return `NULL`, invisibly.
+#' @keywords internal
 #' @export
 check_db_path <- function(.dittodb_env) {
   if (is.null(.dittodb_env$db_path)) {

### 2024-04-09 R/mock-db.R
{dittodb} to `dittodb` to appease CRAN notes

@@ -4,7 +4,7 @@
 #' use fixtures instead of connecting to a real database. Alternatively, you can
 #' start and stop using a mocked database with `start_mock_db()` and
 #' `stop_mock_db()` respectively.to execute the whole thing without needing to
-#' remember to stop the mocking. When testing with {dittodb}, it will look for
+#' remember to stop the mocking. When testing with `dittodb`, it will look for
 #' fixtures in all entries of [`db_mock_paths`].
 #'
 #' You only need to use one approach: either use `start_mock_db()` to start
@@ -17,7 +17,7 @@
 #'
 #' Connections should be made after `start_mock_db()` if you're using that
 #' function or they should be made inside of `with_mock_db()` if you're using
-#' that function because {dittodb} uses the database name (given in `dbname` or
+#' that function because `dittodb` uses the database name (given in `dbname` or
 #' `Database` argument of [`dbConnect`] depending on the driver) to separate
 #' different fixtures. For ODBC connections with only a dsn provided, the dsn is
 #' used for this directory.

### 2024-04-09 R/mock-paths.R

@@ -111,7 +111,7 @@ set_default_db_mock_paths <- function() {
 #' Run the DBI queries in an alternate mock directory
 #'
 #' When testing with dittodb, wrap your tests in `with_mock_path({})` to use the
-#' database fixtures located in other directories. {dittodb} will look for
+#' database fixtures located in other directories. `dittodb` will look for
 #' fixtures in the directory specified by the user, which can be a temporary
 #' or permanent location.
 #'

### 2024-04-09 R/nycflights13-sql.R

@@ -154,11 +154,11 @@ nycflights13_create_sqlite <- function(location = ":memory:", ...) {
 
 #' An SQLite connection to a subset of nycflights13
 #'
-#' Included with {dittodb} is a small subset of
+#' Included with `dittodb` is a small subset of
 #' [`nycflights13`](https://CRAN.R-project.org/package=nycflights13)
 #' prepopulated into a `sqlite` database.
 #'
-#' This database is helpful for getting to know {dittodb} and running example
+#' This database is helpful for getting to know `dittodb` and running example
 #' code. It contains a small subset of the data in nycflights13: namely only the
 #' flights and planes that had a destination of ORD or MDW (the codes for the
 #' two major airports in Chicago) in February of 2013. The airports table has

### 2024-04-09 R/utils.R

@@ -134,18 +134,18 @@ ignore_quotes <- function(statement) {
   return(statement)
 }
 
-#' Set {dittodb}'s debug level
+#' Set `dittodb`'s debug level
 #'
-#' It can be helpful to see what's going on by increasing {dittodb}'s verbosity
+#' It can be helpful to see what's going on by increasing `dittodb`'s verbosity
 #' which will show what's going on under the hood (e.g. what queries are being
 #' requested, from where). This sets the option `dittodb.debug` to the value
 #' given in the `level` argument. The option can be set directly with
 #' `options(dittodb.debug = n)` as well.
 #'
 #' The `level` argument is a numeric, where 0 is the default and (relatively)
-#' silent. The higher the level, the more verbose {dittodb} will be.
+#' silent. The higher the level, the more verbose `dittodb` will be.
 #'
-#' Currently, {dittodb} only has one level of debugging (any value 1 or
+#' Currently, `dittodb` only has one level of debugging (any value 1 or
 #' greater), but more might be used in the future.
 #'
 #' @param level a numeric, the level to set to (e.g. 1)
@@ -194,7 +194,7 @@ get_type <- function(statement) {
 #' Sanitize Table id
 #'
 #' Tables are identified and specified with a large number of ways across
-#' drivers. For the purposes of {dittodb}, the details are less important since
+#' drivers. For the purposes of `dittodb`, the details are less important since
 #' we almost always just want a flat representation (_ie_ for filenames). This
 #' takes the various formats and returns a string with various elements
 #' separated by dots.

### 2024-04-09 R/redact.R
A bit of cleanup (#190)

@@ -1,7 +1,7 @@
 #' Redact columns from a dataframe with the default redactors
 #'
 #' This function redacts the columns specified in `columns` in the data given in
-#' `data` using {dittodb}'s standard redactors.
+#' `data` using `dittodb`'s standard redactors.
 #'
 #' The column names given in the `columns` argument are treated as regular
 #' expressions, however they always have `^` and `$` added to the beginning and
